---
title             : "Regulatory Focus Pride and Covid-19 (Analysis Code)"
author            : "[Author names redacted for blind peer review]"
output:
  pdf_document:
    toc: true
    toc_depth: 2
header-includes:
   - \usepackage[utf8]{inputenc}
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \DeclareUnicodeCharacter{2588}{-}
   - \usepackage{setspace}
   - \usepackage{makecell}
   - \raggedbottom
---

# Setup and Data Cleaning

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = normalizePath('../'))
options(scipen = 999)
```

## Load Libraries and Themes

```{r libs}
# Load libraries
library(knitr) # Required for knitting
library(readxl) # Required to load .xlsx file
library(tidyverse) # Required for data cleaning
library(broman) # Required for myround() function that doesn't truncate digits
library(ggsignif) # Required for plots with significance stars
library(grid) # Required to print plots side by side
library(gridExtra) # Required to print plots side by side

# Load themes
mythemeweb = theme_classic(base_size = 13) +
    theme(legend.position = 'none',
          panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          plot.background = element_rect(fill = "transparent", color = NA),
          panel.background = element_rect(fill = "transparent", color = NA),
          strip.text.x = element_blank(),
          panel.spacing = unit(0.1, "cm"),
          panel.border = element_rect(color="black", fill=NA),
          text = element_text(family="Helvetica", size=13),
          axis.text.x = element_text(size=11, margin=unit(c(5,0,2,0), "mm")),
          axis.text.y = element_text(size=11, margin=unit(c(0,5,0,0), "mm")),
          axis.ticks = element_line(size = .5),
          axis.ticks.length=unit(-2, "mm"))
theme_set(mythemeweb)
```

## Load and Clean Data

```{r clean}
# IMPORT DATA
rf_2019 <- read.csv(file="data/RFQ_Dec2019.csv", header = TRUE)
rf_2020 <- read_excel("data/RAW DATA BeSci Analytic Engine without zipcode.xlsx", col_names = TRUE)
rf_2020b <- read_excel("data/Mindset Survey 1 Data 2020-08-13 Definitions TDJ.xlsx", col_names = TRUE)

## PREPARE DATA FOR CLEANING AND ANALYSIS

# Select RFQ columns from 2019 data
rf_2019 <- rf_2019[,3:24]

# Rename location column
rf_2019 <- dplyr::rename(rf_2019, state = location)

# Remove second header line in 2020 Study 1 data, then rename and grab numeric scores from RFQ columns
rf_2020 <- rf_2020 %>%
  dplyr::filter(RESP_GENDER != "Gender") %>%
  dplyr::rename(gender = RESP_GENDER,
                state = SCREENER1,
                rfq_1 = Q2086001786,
                rfq_2 = Q2073796874,
                rfq_3 = Q2026604185,
                rfq_4 = Q2038294139,
                rfq_5 = Q2097149062,
                rfq_6 = Q2005076527,
                rfq_7 = Q2099986100,
                rfq_8 = Q2014137399,
                rfq_9 = Q2047821109,
                rfq_10 = Q2071138905,
                rfq_11 = Q2082031934,
                ach_pos = Q2005648795,
                prev_neg = Q2064967607,
                rf_moremot = Q2096417839,
                obtainprotect_moremot = Q2061616163,
                foodest_open = Q2078453979,
                foodest_been = Q2015373138,
                foodest_plan = Q2067606070,
                salon_open = Q2029531417,
                salon_been = Q2077930763,
                salon_plan = Q2098211869,
                vitamins = Q2004035326,
                timewithpet = Q2063144300,
                computer_me = Q2071690348__1,
                computer_kids = Q2071690348__2,
                computer_secondhand = Q2071690348__3,
                computer_refurb = Q2071690348__4,
                computer_handdown = Q2071690348__5,
                computer_specupgrade = Q2071690348__6,
                computer_none = Q2071690348__7,
                creditcard = Q2097300961,
                rf_creditcard = Q2035360696,
                lifeins = Q2026863539,
                rf_lifeins = Q2093059946,
                contactless_first = Q2002812802,
                contactless_more = Q2051778461,
                bankapp_first = Q2077157945,
                bankapp_more = Q2060012316,
                rf_shopinperson = Q2001253794,
                target = Q2001547641,
                rf_target = Q2050454100,
                frozenfood = Q2097632970,
                rf_frozenfood = Q2079137883,
                ethnicity = Q2091531022,
                education = Q2057920686,
                income = Q2014095963,
                pol_orient = Q2066820448,
                agegroup = Q2090985821)
rf_2020$rfq_1 <- str_extract(rf_2020$rfq_1, "^.{1}")
rf_2020$rfq_2 <- str_extract(rf_2020$rfq_2, "^.{1}")
rf_2020$rfq_3 <- str_extract(rf_2020$rfq_3, "^.{1}")
rf_2020$rfq_4 <- str_extract(rf_2020$rfq_4, "^.{1}")
rf_2020$rfq_5 <- str_extract(rf_2020$rfq_5, "^.{1}")
rf_2020$rfq_6 <- str_extract(rf_2020$rfq_6, "^.{1}")
rf_2020$rfq_7 <- str_extract(rf_2020$rfq_7, "^.{1}")
rf_2020$rfq_8 <- str_extract(rf_2020$rfq_8, "^.{1}")
rf_2020$rfq_9 <- str_extract(rf_2020$rfq_9, "^.{1}")
rf_2020$rfq_10 <- str_extract(rf_2020$rfq_10, "^.{1}")
rf_2020$rfq_11 <- str_extract(rf_2020$rfq_11, "^.{1}")

rf_2020$state <- str_sub(rf_2020$state, start= -2)

# Do the same for 2020 Study 2 data
rf_2020b <- rf_2020b %>%
  dplyr::filter(RESP_GENDER != "Gender") %>%
  dplyr::rename(gender = RESP_GENDER,
                state = SCREENER1,
                travel_car = "Q2032311582 (Gone on a roadtrip in a car)",
                travel_air = "Q2032311582 (Traveled by airplane)",
                travel_pubtrans = "Q2032311582 (Taken local public transportation (eg bus subwa",
                travel_rideshare = "Q2032311582 (Taken ridesharing services (eg Uber Lyft))",
                travel_taxi = "Q2032311582 (Taken a taxi)",
                stay_hotel = "Q2032311582 (Stayed in a hotel)",
                stay_rental = "Q2032311582 (Stayed in a vacation rental (eg Airbnb))",
                travel_car_l = "Q2040372016 (Go on a roadtrip in a car)",
                travel_air_l = "Q2040372016 (Travel by airplane)",
                travel_pubtrans_l = "Q2040372016 (Take local public transportation (eg bus subway",
                travel_rideshare_l = "Q2040372016 (Take ridesharing services (eg Uber Lyft))",
                travel_taxi_l = "Q2040372016 (Take a taxi)",
                stay_hotel_l = "Q2040372016 (Stay in a hotel)",
                stay_rental_l = "Q2040372016 (Stay in a vacation rental (eg Airbnb))",
                out_restaurant = "Q2038689152 (Gone out to a restaurant with friends/family)",
                out_publicevent = "Q2038689152 (Gone out to an event in public with friends/fam",
                out_bar = "Q2038689152 (Gone out to a bar with friends/family)",
                out_largegathering = "Q2038689152 (Gone out to a large gathering (eg more than 10",
                drank_home = "Q2038689152 (Drank alcoholic beverages at home)",
                online_gathering = "Q2038689152 (Participated in an online social gathering (eg",
                out_restaurant_l = "Q2027016490 (Go out to a restaurant with friends/family)",
                out_publicevent_l = "Q2027016490 (Go out to an event in public with friends/famil",
                out_bar_l = "Q2027016490 (Go out to a bar with friends/family)",
                out_largegathering_l = "Q2027016490 (Go out to a large gathering (eg more than 10 pe",
                drink_home_l = "Q2027016490 (Drink alcoholic beverages at home)",
                online_gathering_l = "Q2027016490 (Participate in an online social gathering (eg Z",
                shop_mall = "Q2007850037 (Gone to a shopping mall)",
                shop_grocery = "Q2007850037 (Gone to a grocery store)",
                order_grocery_delivery = "Q2007850037 (Ordered groceries online for delivery)",
                order_grocery_pickup = "Q2007850037 (Ordered groceries online for pickup)",
                new_prod_brand = "Q2007850037 (Tried a new product or brand for the first time",
                shop_nonessential_instore = "Q2007850037 (Shopped for non-essential items in a store)",
                shop_nonessential_online = "Q2007850037 (Shopped for non-essential items online)",
                shop_mall_l = "Q2074949376 (Go to a shopping mall)",
                shop_grocery_l = "Q2074949376 (Go to a grocery store)",
                order_grocery_delivery_l = "Q2074949376 (Order groceries online for delivery)",
                order_grocery_pickup_l = "Q2074949376 (Order groceries online for pickup)",
                new_prod_brand_l = "Q2074949376 (Try a new product or brand for the first time)",
                shop_nonessential_instore_l = "Q2074949376 (Shop for non-essential items in a store)",
                shop_nonessential_online_l = "Q2074949376 (Shop for non-essential items online)",
                wash_hands_sanitizer = "Q2094454301 (I always wash hands or use hand sanitizer as so",
                wear_mask_self_family = "Q2094454301 (I wear masks whenever I leave my house to prote",
                wear_mask_others = "Q2094454301b (I wear masks whenever I leave my house to prote",
                wear_gloves = "Q2094454301 (I wear gloves whenever I leave my house)",
                social_distancing = "Q2094454301 (I practice social distancing whenever I leave m",
                avoid_places_no_socdist = "Q2094454301 (I avoid going to places that do not enforce soc",
                clean_disinfect = "Q2094454301 (I regularly clean and disinfect my home)",
                tested_covid = "Q2019985903 (Have you been tested for Covid-19 (or antibodie",
                tested_covid_plan = "Q2019985903 (Do you plan to get tested for Covid-19 (or anti",
                covid_threat_personal = "Q2040189607 (What level of threat do you think Covid-19 pose",
                covid_threat_peers = "Q2040189607 (What level of threat do you think Covid-19 pose2",
                life_return_normal = "Q2005528889",
                rfq_1 = "Q2014987959 (Compared to most people are you typically unabl",
                rfq_2 = "Q2014987959 (Do you often do well at different things that y",
                rfq_3 = "Q2014987959 (Not being careful enough has gotten me into tro",
                rfq_4 = "Q2014987959 (Growing up did you ever act in ways that your p",
                rfq_5 = "Q2014987959 (Did you get on your parents’ nerves often when",
                rfq_6 = "Q2014987959 (Growing up would you ever “cross the line” by d",
                rfq_7 = "Q2011014226 (I feel like I have made progress toward being s",
                rfq_8 = "Q2011014226 (I have found very few hobbies or activities in",
                rfq_9 = "Q2076338533",
                rfq_10 = "Q2058289486",
                rfq_11 = "Q2031600708",
                ach_pos_outcomes = "Q2087337059 (I tend to focus on achieving positive outcomes)",
                avoid_neg_cons = "Q2087337059 (I tend to focus on avoiding negative consequenc",
                ach_new_exps = "Q2087337059 (I tend to focus on achieving new experiences)",
                duties_oblig = "Q2087337059 (I tend to focus on my duties and obligations)",
                get_to_do = "Q2087337059 (I tend to focus on things I get to do)",
                have_to_do = "Q2087337059 (I tend to focus on things I have to do)",
                proper_behavior = "Q2016440512 (It is my feeling that if everyone else in a gro",
                avoid_outofstyle = "Q2016440512 (I actively avoid wearing clothes that are not i",
                parties_fit_in = "Q2016440512 (At parties I usually try to behave in a manner",
                uncertain_look_to_others = "Q2016440512 (When I am uncertain how to act in a social situ",
                avoid_outofplace = "Q2016440512 (I try to pay attention to the reactions of othe",
                slang = "Q2016440512 (I find that I tend to pick up slang expressions",
                what_others_wear = "Q2016440512 (I tend to pay attention to what others are wear",
                disapproval_change = "Q2090610647 (The slightest look of disapproval in the eyes o",
                imp_fit_in = "Q2090610647 (Its important to me to fit into the group Im wi",
                beh_depends_on_others = "Q2090610647 (My behavior often depends on how I feel others",
                uncertain_look_to_others2 = "Q2090610647 (If I am the least bit uncertain as to how to ac",
                keep_up_clothing = "Q2090610647 (I usually keep up with clothing style changes b",
                not_follow_crowd = "Q2090610647 (When in a social situation I tend not to follow",
                risks_fun = "Q2017707446 (Taking risks makes life more fun)",
                risk_taker = "Q2017707446 (My friends would say that Im a risk taker)",
                enjoy_risk = "Q2017707446 (I enjoy taking risks in most aspects of my life",
                risk_even_if_hurt = "Q2017707446 (I would take a risk even if it meant I might ge",
                risks_imp = "Q2017707446 (Taking risks is an important part of my life)",
                common_risky_dec = "Q2017707446 (I commonly make risky decisions)",
                believe_taking_chances = "Q2017707446 (I am a believer of taking chances)",
                attracted_by_risk = "Q2017707446 (I am attracted rather than scared by risk)",
                people_listen = "Q2060172177 (I can get people to listen to what I say)",
                wishes_dont_carry_weight = "Q2060172177 (My wishes do not carry much weight)",
                get_others_todo = "Q2060172177 (I can get others to do what I want)",
                views_little_sway = "Q2060172177 (Even if I voice them my views have little sway)",
                have_power = "Q2060172177 (I think I have a great deal of power)",
                ideas_op_ignored = "Q2060172177 (My ideas and opinions are often ignored)",
                unable_get_way = "Q2060172177 (Even when I try I am not able to get my way)",
                make_decisions = "Q2060172177 (If I want to I get to make the decisions)",
                age = "Q2022382998",
                ethnicity = "Q2038877242",
                pol_orient = "Q2058714381",
                education = "Q2066913167",
                income = "Q2035596434")
rf_2020b$rfq_1 <- str_extract(rf_2020b$rfq_1, "^.{1}")
rf_2020b$rfq_2 <- str_extract(rf_2020b$rfq_2, "^.{1}")
rf_2020b$rfq_3 <- str_extract(rf_2020b$rfq_3, "^.{1}")
rf_2020b$rfq_4 <- str_extract(rf_2020b$rfq_4, "^.{1}")
rf_2020b$rfq_5 <- str_extract(rf_2020b$rfq_5, "^.{1}")
rf_2020b$rfq_6 <- str_extract(rf_2020b$rfq_6, "^.{1}")
rf_2020b$rfq_7 <- str_extract(rf_2020b$rfq_7, "^.{1}")
rf_2020b$rfq_8 <- str_extract(rf_2020b$rfq_8, "^.{1}")
rf_2020b$rfq_9 <- str_extract(rf_2020b$rfq_9, "^.{1}")
rf_2020b$rfq_10 <- str_extract(rf_2020b$rfq_10, "^.{1}")
rf_2020b$rfq_11 <- str_extract(rf_2020b$rfq_11, "^.{1}")

# Grab text labels for demographic columns
rf_2020b$ethnicity <- str_sub(rf_2020b$ethnicity, start = 5)
rf_2020b$pol_orient <- str_sub(rf_2020b$pol_orient, start = 5)
rf_2020b$education <- str_sub(rf_2020b$education, start = 5)
rf_2020b$income <- str_sub(rf_2020b$income, start = 5)

# Recode demographics in 2020 Study 2 data to match 2020 Study 1 coding
rf_2020b$pol_orient <- case_when(rf_2020b$pol_orient == "Very conservative" ~ "Strongly Conservative",
                            rf_2020b$pol_orient == "Very liberal" ~ "Strongly Liberal",
                            rf_2020b$pol_orient == "Conservative" ~ "Conservative",
                            rf_2020b$pol_orient == "Liberal" ~ "Liberal",
                            rf_2020b$pol_orient == "Slightly conservative" ~ "Slightly Conservative",
                            rf_2020b$pol_orient == "Slightly liberal" ~ "Slightly Liberal",
                            rf_2020b$pol_orient == "Moderate" ~ "Moderate")
rf_2020b$agegroup <- case_when(rf_2020b$age < 25 ~ "18 - 24",
                              rf_2020b$age < 35 ~ "25 - 34",
                              rf_2020b$age < 45 ~ "35 - 44",
                              rf_2020b$age < 55 ~ "45 - 54",
                              rf_2020b$age < 65 ~ "55 - 64",
                              rf_2020b$age >= 65 ~ "65 or older")
rf_2020b$education <- case_when(rf_2020b$education == "Elementary School" ~ "Other",
                            rf_2020b$education == "Some High School" ~ "Other",
                            rf_2020b$education == "High School Graduate or GED" ~ "High School Diploma",
                            rf_2020b$education == "Some College" ~ "High School Diploma",
                            rf_2020b$education == "Associate Degree" ~ "Associates Degree",
                            rf_2020b$education == "Bachelor’s Degree" ~ "Bachelors Degree",
                            rf_2020b$education == "Master’s Degree" ~ "Graduate Degree",
                            rf_2020b$education == "MD, JD, PhD" ~ "Graduate Degree")
rf_2020b$income <- case_when(rf_2020b$income == "$0-$10,000" ~ "$0 - $10,000",
                            rf_2020b$income == "$10,001 - $20,000" ~ "$10,000 - $20,000",
                            rf_2020b$income == "$20,001 - $40,000" ~ "$20,001 - $40,000",
                            rf_2020b$income == "$40,001 - $70,000" ~ "$40,001 - $70,000",
                            rf_2020b$income == "$70,001 - $100,000" ~ "$70,001 - $100,000",
                            rf_2020b$income == "$100,001 - $250,000" ~ "$100,001 - $250,000",
                            rf_2020b$income == "$250,001+" ~ "$250,001+")

# Add study month columns and then merge dataframes
rf_2020$month <- "Jun"
rf_2020b$month <- "July"
rf_2020 <- merge(rf_2020, rf_2020b, all = T)
rm(rf_2020b)

# Calculate agegroup in 2019 data (consistent with 2020 age group levels)
rf_2019$agegroup <- case_when(rf_2019$age < 25 ~ "18 - 24",
                              rf_2019$age < 35 ~ "25 - 34",
                              rf_2019$age < 45 ~ "35 - 44",
                              rf_2019$age < 55 ~ "45 - 54",
                              rf_2019$age < 65 ~ "55 - 64",
                              rf_2019$age >= 65 ~ "65 or older")
rf_2019$age <- NULL

# Recode demographics in 2019 data to match 2020 coding
rf_2019$income <- case_when(rf_2019$income == "$10K-$20K" ~ "$10,000 - $20,000",
                            rf_2019$income == "$20K-$40K" ~ "$20,001 - $40,000",
                            rf_2019$income == "$40K-$70K" ~ "$40,001 - $70,000",
                            rf_2019$income == "$70K-$100K" ~ "$70,001 - $100,000",
                            rf_2019$income == "$100K-$250K" ~ "$100,001 - $250,000",
                            rf_2019$income == "$250K+" ~ "$250,001+")
rf_2019$education <- case_when(rf_2019$education == "Some High School" ~ "Other",
                            rf_2019$education == "High School" ~ "High School Diploma",
                            rf_2019$education == "Some College" ~ "High School Diploma",
                            rf_2019$education == "Associate's" ~ "Associates Degree",
                            rf_2019$education == "Bachelor's" ~ "Bachelors Degree",
                            rf_2019$education == "Master's" ~ "Graduate Degree",
                            rf_2019$education == "Doctorate" ~ "Graduate Degree",
                            rf_2019$education == "No Response" ~ "Other")
rf_2019$pol_orient <- case_when(rf_2019$pol_orient == "Very Conservative" ~ "Strongly Conservative",
                            rf_2019$pol_orient == "Very Liberal" ~ "Strongly Liberal",
                            rf_2019$pol_orient == "Conservative" ~ "Conservative",
                            rf_2019$pol_orient == "Liberal" ~ "Liberal",
                            rf_2019$pol_orient == "Slightly Conservative" ~ "Slightly Conservative",
                            rf_2019$pol_orient == "Slightly Liberal" ~ "Slightly Liberal",
                            rf_2019$pol_orient == "Moderate" ~ "Moderate")

# Convert RFQ columns to numeric in rf_2020
num <- c("rfq_1", "rfq_2", "rfq_3", "rfq_4", "rfq_5", "rfq_6", 
         "rfq_7", "rfq_8", "rfq_9", "rfq_10", "rfq_11") # Define numeric columns
rf_2020[num] <- lapply(rf_2020[num], as.character) # Convert numeric columns to character (before numeric) to prevent values from changing
rf_2020[num] <- lapply(rf_2020[num], as.numeric) # Convert numeric columns to numeric
rm(num) # Clear mfraw.num from workspace as it is no longer needed

# Add pre vs. post Covid column and then merge dataframes
rf_2019$covid <- "Pre-Covid"
rf_2020$covid <- "Post-Covid"
rf <- bind_rows(rf_2019, rf_2020)
rm(rf_2019, rf_2020)

# Calculate prevention pride and promotion pride scores
rf$prev <- ((6-rf$rfq_2) + (6-rf$rfq_4) + rf$rfq_5 + 
              (6-rf$rfq_6) + (6-rf$rfq_8))/5
rf$prom <- ((6-rf$rfq_1) + rf$rfq_3 + rf$rfq_7 + (6-rf$rfq_9) + 
              rf$rfq_10 + (6-rf$rfq_11))/6

# Calculate promotion dominance scores
rf$promdom <- rf$prom - rf$prev

# Dummy-code pre vs. post Covid
rf$covid.d <- NA
rf$covid.d[rf$covid == "Pre-Covid"] <- 0
rf$covid.d[rf$covid == "Post-Covid"] <- 1

# Create ordered factor version of Covid variable for plotting
rf$covidF <- factor(rf$covid, levels = c("Pre-Covid", "Post-Covid"), ordered = TRUE)

# Create an ordinal numeric version of the political orientation variable and mean-center
rf$pol_orient.num <- dplyr::recode(rf$pol_orient, `Strongly Conservative` = 1, 
                            `Conservative` = 2, `Slightly Conservative` = 3, 
                            `Moderate` = 4, `Slightly Liberal` = 5, 
                            `Liberal` = 6, `Strongly Liberal` = 7, .default = NA_real_)
rf$pol_orient.num.c <- as.numeric(scale(rf$pol_orient.num, center = TRUE, scale = FALSE))

# Create an ordinal numeric version of the age group variable and mean-center
rf$agegroup.num <- dplyr::recode(rf$agegroup, `18 - 24` = 1, `25 - 34` = 2, 
                          `35 - 44` = 3, `45 - 54` = 4, `55 - 64` = 5, 
                          `65 or older` = 6, .default = NA_real_)
rf$agegroup.num.c <- as.numeric(scale(rf$agegroup.num, center = TRUE, scale = FALSE))

## DUMMY-CODE BEHAVIORAL OUTCOME VARIABLES (2020 Study 1)

rf$foodest_open_certain.d <- case_when(rf$foodest_open == "Yes" ~ 1,
                               rf$foodest_open == "Uncertain" ~ 0,
                               rf$foodest_open == "No" ~ 1)
rf$foodest_been.d <- case_when(rf$foodest_been == "Yes" ~ 1,
                               rf$foodest_been == "Does not apply" ~ 0,
                               rf$foodest_been == "No" ~ 0)
rf$foodest_plan.d <- case_when(rf$foodest_plan == "Yes" ~ 1,
                               rf$foodest_plan == "No" ~ 0)
rf$salon_open_certain.d <- case_when(rf$salon_open == "Yes" ~ 1,
                             rf$salon_open == "Uncertain" ~ 0,
                             rf$salon_open == "No" ~ 1)
rf$salon_been.d <- case_when(rf$salon_been == "Yes" ~ 1,
                             rf$salon_been == "Does not apply" ~ 0,
                             rf$salon_been == "No" ~ 0)
rf$salon_plan.d <- case_when(rf$salon_plan == "Yes" ~ 1,
                             rf$salon_plan == "No" ~ 0)
rf$vitamins_current.d <- case_when(rf$vitamins == "Currently using" ~ 1,
                               rf$vitamins == "Considering using" ~ 0,
                               rf$vitamins == "Not considering using" ~ 0)
rf$frozenfood.d <- case_when(rf$frozenfood == "Yes" ~ 1,
                             rf$frozenfood == "No" ~ 0)

# Create Study 1 subsets where needed for analyses
foodest <- filter(rf, foodest_open == "Yes" | foodest_open == "Uncertain") # n = 365
salon <- filter(rf, salon_open == "Yes" | salon_open == "Uncertain") # n = 412


## EXTRACT NUMERIC DATA FOR BEHAVIORAL OUTCOME VARIABLES (2020 Study 2)

# 1 = yes, 2 = no
rf$travel_car <- str_to_title(str_sub(rf$travel_car, start = 5))
rf$travel_air <- str_to_title(str_sub(rf$travel_air, start = 5))
rf$travel_pubtrans <- str_to_title(str_sub(rf$travel_pubtrans, start = 5))
rf$travel_rideshare <- str_to_title(str_sub(rf$travel_rideshare, start = 5))
rf$travel_taxi <- str_to_title(str_sub(rf$travel_taxi, start = 5))
rf$stay_hotel <- str_to_title(str_sub(rf$stay_hotel, start = 5))
rf$stay_rental <- str_to_title(str_sub(rf$stay_rental, start = 5))
rf$out_restaurant <- str_to_title(str_sub(rf$out_restaurant, start = 5))
rf$out_publicevent <- str_to_title(str_sub(rf$out_publicevent, start = 5))
rf$out_bar <- str_to_title(str_sub(rf$out_bar, start = 5))
rf$out_largegathering <- str_to_title(str_sub(rf$out_largegathering, start = 5))
rf$drank_home <- str_to_title(str_sub(rf$drank_home, start = 5))
rf$online_gathering <- str_to_title(str_sub(rf$online_gathering, start = 5))
rf$shop_mall <- str_to_title(str_sub(rf$shop_mall, start = 5))
rf$shop_grocery <- str_to_title(str_sub(rf$shop_grocery, start = 5))
rf$order_grocery_delivery <- str_to_title(str_sub(rf$order_grocery_delivery, start = 5))
rf$order_grocery_pickup <- str_to_title(str_sub(rf$order_grocery_pickup, start = 5))
rf$new_prod_brand <- str_to_title(str_sub(rf$new_prod_brand, start = 5))
rf$shop_nonessential_instore <- str_to_title(str_sub(rf$shop_nonessential_instore, start = 5))
rf$shop_nonessential_online <- str_to_title(str_sub(rf$shop_nonessential_online, start = 5))
rf$tested_covid <- str_to_title(str_sub(rf$tested_covid, start = 5))
rf$tested_covid_plan <- str_to_title(str_sub(rf$tested_covid_plan, start = 5))

# 1 = very unlikely, 7 = very likely
rf$travel_car_l <- str_extract(rf$travel_car_l, "^.{1}")
rf$travel_air_l <- str_extract(rf$travel_air_l, "^.{1}")
rf$travel_pubtrans_l <- str_extract(rf$travel_pubtrans_l, "^.{1}")
rf$travel_rideshare_l <- str_extract(rf$travel_rideshare_l, "^.{1}")
rf$travel_taxi_l <- str_extract(rf$travel_taxi_l, "^.{1}")
rf$stay_hotel_l <- str_extract(rf$stay_hotel_l, "^.{1}")
rf$stay_rental_l <- str_extract(rf$stay_rental_l, "^.{1}")
rf$out_restaurant_l <- str_extract(rf$out_restaurant_l, "^.{1}")
rf$out_publicevent_l <- str_extract(rf$out_publicevent_l, "^.{1}")
rf$out_bar_l <- str_extract(rf$out_bar_l, "^.{1}")
rf$out_largegathering_l <- str_extract(rf$out_largegathering_l, "^.{1}")
rf$drink_home_l <- str_extract(rf$drink_home_l, "^.{1}")
rf$online_gathering_l <- str_extract(rf$online_gathering_l, "^.{1}")
rf$shop_mall_l <- str_extract(rf$shop_mall_l, "^.{1}")
rf$shop_grocery_l <- str_extract(rf$shop_grocery_l, "^.{1}")
rf$order_grocery_delivery_l <- str_extract(rf$order_grocery_delivery_l, "^.{1}")
rf$order_grocery_pickup_l <- str_extract(rf$order_grocery_pickup_l, "^.{1}")
rf$new_prod_brand_l <- str_extract(rf$new_prod_brand_l, "^.{1}")
rf$shop_nonessential_instore_l <- str_extract(rf$shop_nonessential_instore_l, "^.{1}")
rf$shop_nonessential_online_l <- str_extract(rf$shop_nonessential_online_l, "^.{1}")

# 1 = strongly disagree, 7 = strongly agree
rf$wash_hands_sanitizer <- str_extract(rf$wash_hands_sanitizer, "^.{1}")
rf$wear_mask_self_family <- str_extract(rf$wear_mask_self_family, "^.{1}")
rf$wear_mask_others <- str_extract(rf$wear_mask_others, "^.{1}")
rf$wear_gloves <- str_extract(rf$wear_gloves, "^.{1}")
rf$social_distancing <- str_extract(rf$social_distancing, "^.{1}")
rf$avoid_places_no_socdist <- str_extract(rf$avoid_places_no_socdist, "^.{1}")
rf$clean_disinfect <- str_extract(rf$clean_disinfect, "^.{1}")
rf$risks_fun <- str_extract(rf$risks_fun, "^.{1}")
rf$risk_taker <- str_extract(rf$risk_taker, "^.{1}")
rf$enjoy_risk <- str_extract(rf$enjoy_risk, "^.{1}")
rf$risk_even_if_hurt <- str_extract(rf$risk_even_if_hurt, "^.{1}")
rf$risks_imp <- str_extract(rf$risks_imp, "^.{1}")
rf$common_risky_dec <- str_extract(rf$common_risky_dec, "^.{1}")
rf$believe_taking_chances <- str_extract(rf$believe_taking_chances, "^.{1}")
rf$attracted_by_risk <- str_extract(rf$attracted_by_risk, "^.{1}")
rf$people_listen <- str_extract(rf$people_listen, "^.{1}")
rf$wishes_dont_carry_weight <- str_extract(rf$wishes_dont_carry_weight, "^.{1}")
rf$get_others_todo <- str_extract(rf$get_others_todo, "^.{1}")
rf$views_little_sway <- str_extract(rf$views_little_sway, "^.{1}")
rf$have_power <- str_extract(rf$have_power, "^.{1}")
rf$ideas_op_ignored <- str_extract(rf$ideas_op_ignored, "^.{1}")
rf$unable_get_way <- str_extract(rf$unable_get_way, "^.{1}")
rf$make_decisions <- str_extract(rf$make_decisions, "^.{1}")

# 1 = very low threat, 7 = very high threat
rf$covid_threat_personal <- str_extract(rf$covid_threat_personal, "^.{1}")
rf$covid_threat_peers <- str_extract(rf$covid_threat_peers, "^.{1}")

rf$state <- str_sub(rf$state, start= -2)

# 1 = strongly disagree, 5 = strongly agree
rf$ach_pos_outcomes <- str_extract(rf$ach_pos_outcomes, "^.{1}")
rf$avoid_neg_cons <- str_extract(rf$avoid_neg_cons, "^.{1}")
rf$ach_new_exps <- str_extract(rf$ach_new_exps, "^.{1}")
rf$duties_oblig <- str_extract(rf$duties_oblig, "^.{1}")
rf$get_to_do <- str_extract(rf$get_to_do, "^.{1}")
rf$have_to_do <- str_extract(rf$have_to_do, "^.{1}")

# 1 = always false, 7 = always true
rf$proper_behavior <- str_extract(rf$proper_behavior, "^.{1}")
rf$avoid_outofstyle <- str_extract(rf$avoid_outofstyle, "^.{1}")
rf$parties_fit_in <- str_extract(rf$parties_fit_in, "^.{1}")
rf$uncertain_look_to_others <- str_extract(rf$uncertain_look_to_others, "^.{1}")
rf$avoid_outofplace <- str_extract(rf$avoid_outofplace, "^.{1}")
rf$slang <- str_extract(rf$slang, "^.{1}")
rf$what_others_wear <- str_extract(rf$what_others_wear, "^.{1}")
rf$disapproval_change <- str_extract(rf$disapproval_change, "^.{1}")
rf$imp_fit_in <- str_extract(rf$imp_fit_in, "^.{1}")
rf$beh_depends_on_others <- str_extract(rf$beh_depends_on_others, "^.{1}")
rf$uncertain_look_to_others2 <- str_extract(rf$uncertain_look_to_others2, "^.{1}")
rf$keep_up_clothing <- str_extract(rf$keep_up_clothing, "^.{1}")
rf$not_follow_crowd <- str_extract(rf$not_follow_crowd, "^.{1}")

# Recode life_return_normal columns
rf$life_return_normal <- case_when(rf$life_return_normal == "It has already been contained" ~ 1,
                             rf$life_return_normal == "1-2 months from now" ~ 2,
                             rf$life_return_normal == "3-5 months from now" ~ 3,
                             rf$life_return_normal == "6-8 months from now " ~ 4,
                             rf$life_return_normal == "9-12 months from now" ~ 5,
                             rf$life_return_normal == "More than 12 months from now" ~ 6)

# Dummy-code 2020 Study 2 behavioral outcome variables
rf$travel_car.d <- case_when(rf$travel_car == "Yes" ~ 1,
                             rf$travel_car == "No" ~ 0)
rf$travel_air.d <- case_when(rf$travel_air == "Yes" ~ 1,
                             rf$travel_air == "No" ~ 0)
rf$travel_pubtrans.d <- case_when(rf$travel_pubtrans == "Yes" ~ 1,
                             rf$travel_pubtrans == "No" ~ 0)
rf$travel_rideshare.d <- case_when(rf$travel_rideshare == "Yes" ~ 1,
                             rf$travel_rideshare == "No" ~ 0)
rf$travel_taxi.d <- case_when(rf$travel_taxi == "Yes" ~ 1,
                             rf$travel_taxi == "No" ~ 0)
rf$stay_hotel.d <- case_when(rf$stay_hotel == "Yes" ~ 1,
                             rf$stay_hotel == "No" ~ 0)
rf$stay_rental.d <- case_when(rf$stay_rental == "Yes" ~ 1,
                             rf$stay_rental == "No" ~ 0)
rf$out_restaurant.d <- case_when(rf$out_restaurant == "Yes" ~ 1,
                             rf$out_restaurant == "No" ~ 0)
rf$out_publicevent.d <- case_when(rf$out_publicevent == "Yes" ~ 1,
                             rf$out_publicevent == "No" ~ 0)
rf$out_bar.d <- case_when(rf$out_bar == "Yes" ~ 1,
                             rf$out_bar == "No" ~ 0)
rf$out_largegathering.d <- case_when(rf$out_largegathering == "Yes" ~ 1,
                             rf$out_largegathering == "No" ~ 0)
rf$drank_home.d <- case_when(rf$drank_home == "Yes" ~ 1,
                             rf$drank_home == "No" ~ 0)
rf$online_gathering.d <- case_when(rf$online_gathering == "Yes" ~ 1,
                             rf$online_gathering == "No" ~ 0)
rf$shop_mall.d <- case_when(rf$shop_mall == "Yes" ~ 1,
                             rf$shop_mall == "No" ~ 0)
rf$shop_grocery.d <- case_when(rf$shop_grocery == "Yes" ~ 1,
                             rf$shop_grocery == "No" ~ 0)
rf$order_grocery_delivery.d <- case_when(rf$order_grocery_delivery == "Yes" ~ 1,
                             rf$order_grocery_delivery == "No" ~ 0)
rf$order_grocery_pickup.d <- case_when(rf$order_grocery_pickup == "Yes" ~ 1,
                             rf$order_grocery_pickup == "No" ~ 0)
rf$new_prod_brand.d <- case_when(rf$new_prod_brand == "Yes" ~ 1,
                             rf$new_prod_brand == "No" ~ 0)
rf$shop_nonessential_instore.d <- case_when(rf$shop_nonessential_instore == "Yes" ~ 1,
                             rf$shop_nonessential_instore == "No" ~ 0)
rf$shop_nonessential_online.d <- case_when(rf$shop_nonessential_online == "Yes" ~ 1,
                             rf$shop_nonessential_online == "No" ~ 0)
rf$tested_covid.d <- case_when(rf$tested_covid == "Yes" ~ 1,
                             rf$tested_covid == "No" ~ 0)
rf$tested_covid_plan.d <- case_when(rf$tested_covid_plan == "Yes" ~ 1,
                             rf$tested_covid_plan == "No" ~ 0)

# Create numeric month variable
rf$month.num[rf$covid == "Pre-Covid"] <- 1 # December 2019
rf$month.num[rf$covid == "Post-Covid" & rf$month == "Jun"] <- 7 # June 2020
rf$month.num[rf$covid == "Post-Covid" & rf$month == "July"] <- 8 # July 2020

# Make character month variable an ordered factor
rf$month <- factor(rf$month, levels=c("Jun", "July"), ordered=TRUE)

# Convert numeric columns to numeric
num <- c("ach_pos_outcomes", "rf_moremot", "obtainprotect_moremot", "travel_car_l", "travel_air_l", "travel_pubtrans_l", "travel_rideshare_l", "travel_taxi_l", "stay_hotel_l", "stay_rental_l", "out_restaurant_l", "out_publicevent_l", "out_bar_l", "out_largegathering_l", "drink_home_l", "online_gathering_l", "shop_mall_l", "shop_grocery_l", "order_grocery_delivery_l", "order_grocery_pickup_l", "new_prod_brand_l", "shop_nonessential_instore_l", "shop_nonessential_online_l", "wash_hands_sanitizer", "wear_mask_self_family", "wear_mask_others", "wear_gloves", "social_distancing", "avoid_places_no_socdist", "clean_disinfect", "covid_threat_personal", "covid_threat_peers", "life_return_normal", "avoid_neg_cons", "ach_new_exps", "duties_oblig", "get_to_do", "have_to_do", "proper_behavior", "avoid_outofstyle", "parties_fit_in", "uncertain_look_to_others", "avoid_outofplace", "slang", "what_others_wear", "disapproval_change", "imp_fit_in", "beh_depends_on_others", "uncertain_look_to_others2", "keep_up_clothing", "not_follow_crowd", "risks_fun", "risk_taker", "enjoy_risk", "risk_even_if_hurt", "risks_imp", "common_risky_dec", "believe_taking_chances", "attracted_by_risk", "people_listen", "wishes_dont_carry_weight", "get_others_todo", "views_little_sway", "have_power", "ideas_op_ignored", "unable_get_way", "make_decisions", "age") # Define numeric columns
rf[num] <- lapply(rf[num], as.character) # Convert numeric columns to character (before numeric) to prevent values from changing
rf[num] <- lapply(rf[num], as.numeric) # Convert numeric columns to numeric
rm(num) # Clear mfraw.num from workspace as it is no longer needed

## CREATE 2019 AND 2020 SUBSETS

rf_2019 <- dplyr::filter(rf, covid == "Pre-Covid")
rf_2020 <- dplyr::filter(rf, covid == "Post-Covid")
rf_2020a <- dplyr::filter(rf, covid == "Post-Covid" & month == "Jun")
rf_2020b <- dplyr::filter(rf, covid == "Post-Covid" & month == "July")
```

# Participants

## 2019 Data (Pre-Covid-19 Pandemic)

```{r rf_2019_ps}
# Gender
male <- sum(rf_2019$gender == "Male", na.rm = T) # n = 143
female <- sum(rf_2019$gender == "Female", na.rm = T) # n = 135
malepct <- round(male/nrow(rf_2019)*100, digits = 0) # 51%
femalepct <- round(female/nrow(rf_2019)*100, digits = 0) # 48%

# Age Group
eighteen24 <- round(nrow(filter(rf_2019, agegroup == "18 - 24"))/
                      nrow(rf_2019)*100, digits = 0) # 8%
twentyfive34 <- round(nrow(filter(rf_2019, agegroup == "25 - 34"))/
                        nrow(rf_2019)*100, digits = 0) # 42%
thirtyfive44 <- round(nrow(filter(rf_2019, agegroup == "35 - 44"))/
                        nrow(rf_2019)*100, digits = 0) # 29%
fortyfive54 <- round(nrow(filter(rf_2019, agegroup == "45 - 54"))/
                       nrow(rf_2019)*100, digits = 0) # 12%
fiftyfive64 <- round(nrow(filter(rf_2019, agegroup == "55 - 64"))/
                       nrow(rf_2019)*100, digits = 0) # 6%
sixtyfiveplus <- round(nrow(filter(rf_2019, agegroup == "65 or older"))/
                         nrow(rf_2019)*100, digits = 0) # 3%

# Income
ten20 <- round(nrow(filter(rf_2019, income == "$10,000 - $20,000"))/nrow(rf_2019)*100, digits = 0) # 5%
twenty40 <- round(nrow(filter(rf_2019, income == "$20,001 - $40,000"))/nrow(rf_2019)*100, digits = 0) # 24%
forty70 <- round(nrow(filter(rf_2019, income == "$40,001 - $70,000"))/nrow(rf_2019)*100, digits = 0) # 28%
seventy100 <- round(nrow(filter(rf_2019, income == "$70,001 - $100,000"))/nrow(rf_2019)*100, digits = 0) # 22%
hundred250 <- round(nrow(filter(rf_2019, income == "$100,001 - $250,000"))/nrow(rf_2019)*100, digits = 0) # 15%

# Education
highschool <- round(nrow(filter(rf_2019, education == "High School Diploma"))/nrow(rf_2019)*100, digits = 0) # 36%
associates <- round(nrow(filter(rf_2019, education == "Associates Degree"))/nrow(rf_2019)*100, digits = 0) # 15%
bachelors <- round(nrow(filter(rf_2019, education == "Bachelors Degree"))/nrow(rf_2019)*100, digits = 0) # 38%
grad <- round(nrow(filter(rf_2019, education == "Graduate Degree"))/nrow(rf_2019)*100, digits = 0) # 10%
edother <- round(nrow(filter(rf_2019, education == "Other"))/nrow(rf_2019)*100, digits = 0) # <1%

# Political Orientation
stronglycons <- round(nrow(filter(rf_2019, pol_orient == "Strongly Conservative"))/
                        nrow(rf_2019)*100, digits = 0) # 4%
cons <- round(nrow(filter(rf_2019, pol_orient == "Conservative"))/
                nrow(rf_2019)*100, digits = 0) # 11%
slightlycons <- round(nrow(filter(rf_2019, pol_orient == "Slightly Conservative"))/
                        nrow(rf_2019)*100, digits = 0) # 11%
moderate <- round(nrow(filter(rf_2019, pol_orient == "Moderate"))/
                    nrow(rf_2019)*100, digits = 0) # 18%
slightlylib <- round(nrow(filter(rf_2019, pol_orient == "Slightly Liberal"))/
                       nrow(rf_2019)*100, digits = 0) # 15%
lib <- round(nrow(filter(rf_2019, pol_orient == "Liberal"))/
               nrow(rf_2019)*100, digits = 0) # 22%
stronglylib <- round(nrow(filter(rf_2019, pol_orient == "Strongly Liberal"))/
                       nrow(rf_2019)*100, digits = 0) # 18%
```

## 2020 Study 1 Data (Post-Covid-19 Pandemic)

```{r rf_2020a_ps}
# Gender
male <- sum(rf_2020a$gender == "Male", na.rm = T) # n = 294
female <- sum(rf_2020a$gender == "Female", na.rm = T) # n = 306
malepct <- round(male/nrow(rf_2020a)*100, digits = 0) # 49%
femalepct <- round(female/nrow(rf_2020a)*100, digits = 0) # 51%

# Age Group
eighteen24 <- round(nrow(filter(rf_2020a, agegroup == "18 - 24"))/
                      nrow(rf_2020a)*100, digits = 0) # 8%
twentyfive34 <- round(nrow(filter(rf_2020a, agegroup == "25 - 34"))/
                        nrow(rf_2020a)*100, digits = 0) # 27%
thirtyfive44 <- round(nrow(filter(rf_2020a, agegroup == "35 - 44"))/
                        nrow(rf_2020a)*100, digits = 0) # 8%
fortyfive54 <- round(nrow(filter(rf_2020a, agegroup == "45 - 54"))/
                       nrow(rf_2020a)*100, digits = 0) # 16%
fiftyfive64 <- round(nrow(filter(rf_2020a, agegroup == "55 - 64"))/
                       nrow(rf_2020a)*100, digits = 0) # 35%
sixtyfiveplus <- round(nrow(filter(rf_2020a, agegroup == "65 or older"))/
                         nrow(rf_2020a)*100, digits = 0) # 6%

# Income
zero10 <- round(nrow(filter(rf_2020a, income == "$0 - $10,000"))/nrow(rf_2020a)*100, digits = 0) # 8%
ten20 <- round(nrow(filter(rf_2020a, income == "$10,000 - $20,000"))/nrow(rf_2020a)*100, digits = 0) # 9%
twenty40 <- round(nrow(filter(rf_2020a, income == "$20,001 - $40,000"))/nrow(rf_2020a)*100, digits = 0) # 22%
forty70 <- round(nrow(filter(rf_2020a, income == "$40,001 - $70,000"))/nrow(rf_2020a)*100, digits = 0) # 24%
seventy100 <- round(nrow(filter(rf_2020a, income == "$70,001 - $100,000"))/nrow(rf_2020a)*100, digits = 0) # 18%
hundred250 <- round(nrow(filter(rf_2020a, income == "$100,001 - $250,000"))/nrow(rf_2020a)*100, digits = 0) # 17%
twofiftyplus <- round(nrow(filter(rf_2020a, income == "$250,001+"))/nrow(rf_2020a)*100, digits = 0) # 3%

# Education
highschool <- round(nrow(filter(rf_2020a, education == "High School Diploma"))/nrow(rf_2020a)*100, digits = 0) # 27%
associates <- round(nrow(filter(rf_2020a, education == "Associates Degree"))/nrow(rf_2020a)*100, digits = 0) # 17%
bachelors <- round(nrow(filter(rf_2020a, education == "Bachelors Degree"))/nrow(rf_2020a)*100, digits = 0) # 33%
grad <- round(nrow(filter(rf_2020a, education == "Graduate Degree"))/nrow(rf_2020a)*100, digits = 0) # 18%
edother <- round(nrow(filter(rf_2020a, education == "Other"))/nrow(rf_2020a)*100, digits = 0) # 5%

# Political Orientation
stronglycons <- round(nrow(filter(rf_2020a, pol_orient == "Strongly Conservative"))/
                        nrow(rf_2020a)*100, digits = 0) # 11%
cons <- round(nrow(filter(rf_2020a, pol_orient == "Conservative"))/
                nrow(rf_2020a)*100, digits = 0) # 16%
slightlycons <- round(nrow(filter(rf_2020a, pol_orient == "Slightly Conservative"))/
                        nrow(rf_2020a)*100, digits = 0) # 10%
moderate <- round(nrow(filter(rf_2020a, pol_orient == "Moderate"))/
                    nrow(rf_2020a)*100, digits = 0) # 36%
slightlylib <- round(nrow(filter(rf_2020a, pol_orient == "Slightly Liberal"))/
                       nrow(rf_2020a)*100, digits = 0) # 8%
lib <- round(nrow(filter(rf_2020a, pol_orient == "Liberal"))/
               nrow(rf_2020a)*100, digits = 0) # 10%
stronglylib <- round(nrow(filter(rf_2020a, pol_orient == "Strongly Liberal"))/
                       nrow(rf_2020a)*100, digits = 0) # 9%
```

## 2020 Study 2 Data (Post-Covid-19 Pandemic)

```{r rf_2020b_ps}
# Gender
male <- sum(rf_2020b$gender == "Male", na.rm = T) # n = 294
female <- sum(rf_2020b$gender == "Female", na.rm = T) # n = 306
malepct <- round(male/nrow(rf_2020b)*100, digits = 0) # 49%
femalepct <- round(female/nrow(rf_2020b)*100, digits = 0) # 51%

# Age Group
eighteen24 <- round(nrow(filter(rf_2020b, agegroup == "18 - 24"))/
                      nrow(rf_2020b)*100, digits = 0) # 8%
twentyfive34 <- round(nrow(filter(rf_2020b, agegroup == "25 - 34"))/
                        nrow(rf_2020b)*100, digits = 0) # 28%
thirtyfive44 <- round(nrow(filter(rf_2020b, agegroup == "35 - 44"))/
                        nrow(rf_2020b)*100, digits = 0) # 8%
fortyfive54 <- round(nrow(filter(rf_2020b, agegroup == "45 - 54"))/
                       nrow(rf_2020b)*100, digits = 0) # 13%
fiftyfive64 <- round(nrow(filter(rf_2020b, agegroup == "55 - 64"))/
                       nrow(rf_2020b)*100, digits = 0) # 39%
sixtyfiveplus <- round(nrow(filter(rf_2020b, agegroup == "65 or older"))/
                         nrow(rf_2020b)*100, digits = 0) # 3%

# Income
zero10 <- round(nrow(filter(rf_2020b, income == "$0 - $10,000"))/nrow(rf_2020b)*100, digits = 0) # 5%
ten20 <- round(nrow(filter(rf_2020b, income == "$10,000 - $20,000"))/nrow(rf_2020b)*100, digits = 0) # 6%
twenty40 <- round(nrow(filter(rf_2020b, income == "$20,001 - $40,000"))/nrow(rf_2020b)*100, digits = 0) # 16%
forty70 <- round(nrow(filter(rf_2020b, income == "$40,001 - $70,000"))/nrow(rf_2020b)*100, digits = 0) # 28%
seventy100 <- round(nrow(filter(rf_2020b, income == "$70,001 - $100,000"))/nrow(rf_2020b)*100, digits = 0) # 20%
hundred250 <- round(nrow(filter(rf_2020b, income == "$100,001 - $250,000"))/nrow(rf_2020b)*100, digits = 0) # 22%
twofiftyplus <- round(nrow(filter(rf_2020b, income == "$250,001+"))/nrow(rf_2020b)*100, digits = 0) # 2%

# Education
highschool <- round(nrow(filter(rf_2020b, education == "High School Diploma"))/nrow(rf_2020b)*100, digits = 0) # 35%
associates <- round(nrow(filter(rf_2020b, education == "Associates Degree"))/nrow(rf_2020b)*100, digits = 0) # 11%
bachelors <- round(nrow(filter(rf_2020b, education == "Bachelors Degree"))/nrow(rf_2020b)*100, digits = 0) # 36%
grad <- round(nrow(filter(rf_2020b, education == "Graduate Degree"))/nrow(rf_2020b)*100, digits = 0) # 17%
edother <- round(nrow(filter(rf_2020b, education == "Other"))/nrow(rf_2020b)*100, digits = 0) # 2%

# Political Orientation
stronglycons <- round(nrow(filter(rf_2020b, pol_orient == "Strongly Conservative"))/
                        nrow(rf_2020b)*100, digits = 0) # 8%
cons <- round(nrow(filter(rf_2020b, pol_orient == "Conservative"))/
                nrow(rf_2020b)*100, digits = 0) # 14%
slightlycons <- round(nrow(filter(rf_2020b, pol_orient == "Slightly Conservative"))/
                        nrow(rf_2020b)*100, digits = 0) # 11%
moderate <- round(nrow(filter(rf_2020b, pol_orient == "Moderate"))/
                    nrow(rf_2020b)*100, digits = 0) # 35%
slightlylib <- round(nrow(filter(rf_2020b, pol_orient == "Slightly Liberal"))/
                       nrow(rf_2020b)*100, digits = 0) # 8%
lib <- round(nrow(filter(rf_2020b, pol_orient == "Liberal"))/
               nrow(rf_2020b)*100, digits = 0) # 13%
stronglylib <- round(nrow(filter(rf_2020b, pol_orient == "Strongly Liberal"))/
                       nrow(rf_2020b)*100, digits = 0) # 10%
```

# Regulatory Focus Questionnaire: Summary Statistics

## 2019 Data (Pre-Covid-19 Pandemic)

```{r rf_2019_rf}
prommean <- myround(mean(rf_2019$prom, na.rm = T), digits = 2) # 3.59
promsd <- myround(sd(rf_2019$prom, na.rm = T), digits = 2) # 0.71
prom <- select(rf_2019, rfq_1, rfq_3, rfq_7, rfq_9, rfq_10, rfq_11)
prom$rfq_1 <- 6 - prom$rfq_1
prom$rfq_9 <- 6 - prom$rfq_9
prom$rfq_11 <- 6 - prom$rfq_11
promalpha <- myround(psych::alpha(prom, check.keys = TRUE)$total["raw_alpha"],
                     digits = 2) # 0.74

prevmean <- myround(mean(rf_2019$prev, na.rm = T), digits = 2) # 3.43
prevsd <- myround(sd(rf_2019$prev, na.rm = T), digits = 2) # 0.84
prev <- select(rf_2019, rfq_2, rfq_4, rfq_5, rfq_6, rfq_8)
prev$rfq_2 <- 6 - prev$rfq_2
prev$rfq_4 <- 6 - prev$rfq_4
prev$rfq_6 <- 6 - prev$rfq_6
prev$rfq_8 <- 6 - prev$rfq_8
prevalpha <- myround(psych::alpha(prev, check.keys = TRUE)$total["raw_alpha"],
                     digits = 2) # 0.84
```

## 2020 Study 1 Data (Post-Covid-19 Pandemic)

```{r rf_2020a_rf}
prommean <- myround(mean(rf_2020a$prom, na.rm = T), digits = 2) # 3.46
promsd <- myround(sd(rf_2020a$prom, na.rm = T), digits = 2) # 0.62
prom <- select(rf_2020a, rfq_1, rfq_3, rfq_7, rfq_9, rfq_10, rfq_11)
prom$rfq_1 <- 6 - prom$rfq_1
prom$rfq_9 <- 6 - prom$rfq_9
prom$rfq_11 <- 6 - prom$rfq_11
promalpha <- myround(psych::alpha(prom, check.keys = TRUE)$total["raw_alpha"], 
                     digits = 2) # 0.63

prevmean <- myround(mean(rf_2020a$prev, na.rm = T), digits = 2) # 3.40
prevsd <- myround(sd(rf_2020a$prev, na.rm = T), digits = 2) # 0.81
prev <- select(rf_2020a, rfq_2, rfq_4, rfq_5, rfq_6, rfq_8)
prev$rfq_2 <- 6 - prev$rfq_2
prev$rfq_4 <- 6 - prev$rfq_4
prev$rfq_6 <- 6 - prev$rfq_6
prev$rfq_8 <- 6 - prev$rfq_8
prevalpha <- myround(psych::alpha(prev, check.keys = TRUE)$total["raw_alpha"], 
                     digits = 2) # 0.80
```

## 2020 Study 2 Data (Post-Covid-19 Pandemic)

```{r rf_2020b_rf}
prommean <- myround(mean(rf_2020b$prom, na.rm = T), digits = 2) # 2.85
promsd <- myround(sd(rf_2020b$prom, na.rm = T), digits = 2) # 0.35
prom <- select(rf_2020b, rfq_1, rfq_3, rfq_7, rfq_9, rfq_10, rfq_11)
prom$rfq_1 <- 6 - prom$rfq_1
prom$rfq_9 <- 6 - prom$rfq_9
prom$rfq_11 <- 6 - prom$rfq_11
promalpha <- myround(psych::alpha(prom, check.keys = TRUE)$total["raw_alpha"], 
                     digits = 2) # 0.61

prevmean <- myround(mean(rf_2020b$prev, na.rm = T), digits = 2) # 3.02
prevsd <- myround(sd(rf_2020b$prev, na.rm = T), digits = 2) # 0.46
prev <- select(rf_2020b, rfq_2, rfq_4, rfq_5, rfq_6, rfq_8)
prev$rfq_2 <- 6 - prev$rfq_2
prev$rfq_4 <- 6 - prev$rfq_4
prev$rfq_6 <- 6 - prev$rfq_6
prev$rfq_8 <- 6 - prev$rfq_8
prevalpha <- myround(psych::alpha(prev, check.keys = TRUE)$total["raw_alpha"], 
                     digits = 2) # 0.59
```

# Study 1 Results

## Differences in Regulatory Focus Before Versus After Start of Covid-19 Pandemic

```{r s1_prom_diff}
prom.covid <- lm(prom ~ covid.d + agegroup.num.c + pol_orient.num.c, data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")))
summary(prom.covid)
prom.covid.data <- summary(prom.covid)$coefficients

prom.covid.b <- prom.covid.data["covid.d", "Estimate"]
prom.covid.se <- prom.covid.data["covid.d", "Std. Error"]
prom.covid.t <- prom.covid.data["covid.d", "t value"]
prom.covid.df <- summary(prom.covid)$df[2]
prom.covid.p <- prom.covid.data["covid.d", "Pr(>|t|)"]

confint(prom.covid)
```

```{r s1_prev_diff}
prev.covid <- lm(prev ~ covid.d + agegroup.num.c + pol_orient.num.c, data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")))
summary(prev.covid)
prev.covid.data <- summary(prev.covid)$coefficients

prev.covid.b <- prev.covid.data["covid.d", "Estimate"]
prev.covid.se <- prev.covid.data["covid.d", "Std. Error"]
prev.covid.t <- prev.covid.data["covid.d", "t value"]
prev.covid.df <- summary(prev.covid)$df[2]
prev.covid.p <- prev.covid.data["covid.d", "Pr(>|t|)"]

confint(prev.covid)
```

```{r s1_aim1_plots}
# Determining pre- vs. post-Covid predictions at typical 
# levels of age group and political orientation
pred <- data.frame(
  covidF = c("Pre-Covid", "Post-Covid"),
  covid.d = c(0, 1),
  agegroup.num.c = 0,
  pol_orient.num.c = 0)
prompred <- cbind(pred, predict(prom.covid, pred, se.fit = TRUE))
prevpred <- cbind(pred, predict(prev.covid, pred, se.fit = TRUE))

promplot <- ggplot(data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")), aes(x = covidF, y = prom)) +
  geom_point(alpha = .15, color = "seagreen3", 
             position = position_jitter(height = .05, width = .2)) +
  geom_point(data = prompred, aes(x = covidF, y = fit), color = "black", size = 1.5) +
  geom_errorbar(data = prompred, aes(x = covidF, y = fit, ymin = fit - se.fit, ymax = fit + se.fit),
                width = .4, color = "black", size = .4) +
  geom_signif(y_position = c(4.2), xmin = c(1), xmax = c(2), annotation = c("***"),
              textsize = 6, color = "black", vjust = -.4) +
  scale_y_continuous(limits = c(1, 5)) +
  annotate("text", x = .6, y = 1.5, label = "a", size = 9) +
  labs(x = "Pre- Versus Post-Covid-19", y = "Promotion Pride")

prevplot <- ggplot(data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")), aes(x = covidF, y = prev)) +
  geom_point(alpha = .15, color = "lightcoral",
             position = position_jitter(height = .05, width = .2)) +
  geom_point(data = prevpred, aes(x = covidF, y = fit), color = "black", size = 1.5) +
  geom_errorbar(data = prevpred, aes(x = covidF, y = fit, ymin = fit - se.fit, ymax = fit + se.fit),
                width = .4, color = "black", size = .4) +
  geom_signif(y_position = c(4.2), xmin = c(1), xmax = c(2), annotation = c("*"),
              textsize = 6, color = "black", vjust = -.4) +
  scale_y_continuous(limits = c(1, 5)) +
  annotate("text", x = .6, y = 1.5, label = "b", size = 9) +
  labs(x = "Pre- Versus Post-Covid-19", y = "Prevention Pride")
```

Figure 1: Model-predicted differences in promotion pride and prevention pride before versus after the start of the Covid-19 pandemic, at typical levels of age group and political ideology. Error bars represent standard errors of the mean.

```{r fig1, include = TRUE, fig.align = "center"}
grid.arrange(promplot, prevplot, ncol=2, heights = c(3, 3), widths = c(4, 4))
```

## Associations Between Post-Covid-19 Regulatory Focus Pride and Behavioral Outcomes

### Actively Searching for Information About the Opening of the Market

```{r foodest_open}
foodest_open.rf <- glm(foodest_open_certain.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                       data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")), family = "binomial")
summary(foodest_open.rf)
foodest_open.rf.data <- summary(foodest_open.rf)$coefficients

foodest_open.rf.prom.b <- foodest_open.rf.data["prom", "Estimate"]
foodest_open.rf.prom.se <- foodest_open.rf.data["prom", "Std. Error"]
foodest_open.rf.prom.z <- foodest_open.rf.data["prom", "z value"]
foodest_open.rf.prom.df <- summary(foodest_open.rf)$df[2]
foodest_open.rf.prom.p <- foodest_open.rf.data["prom", "Pr(>|z|)"]
foodest_open.rf.prom.or <- exp(foodest_open.rf.prom.b)

foodest_open.rf.prev.b <- foodest_open.rf.data["prev", "Estimate"]
foodest_open.rf.prev.se <- foodest_open.rf.data["prev", "Std. Error"]
foodest_open.rf.prev.z <- foodest_open.rf.data["prev", "z value"]
foodest_open.rf.prev.df <- summary(foodest_open.rf)$df[2]
foodest_open.rf.prev.p <- foodest_open.rf.data["prev", "Pr(>|z|)"]
foodest_open.rf.prev.or <- exp(foodest_open.rf.prev.b)

confint(foodest_open.rf)
```

```{r salon_open}
salon_open.rf <- glm(salon_open_certain.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                     data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")), family = "binomial")
summary(salon_open.rf)
salon_open.rf.data <- summary(salon_open.rf)$coefficients

salon_open.rf.prom.b <- salon_open.rf.data["prom", "Estimate"]
salon_open.rf.prom.se <- salon_open.rf.data["prom", "Std. Error"]
salon_open.rf.prom.z <- salon_open.rf.data["prom", "z value"]
salon_open.rf.prom.df <- summary(salon_open.rf)$df[2]
salon_open.rf.prom.p <- salon_open.rf.data["prom", "Pr(>|z|)"]
salon_open.rf.prom.or <- exp(salon_open.rf.prom.b)

salon_open.rf.prev.b <- salon_open.rf.data["prev", "Estimate"]
salon_open.rf.prev.se <- salon_open.rf.data["prev", "Std. Error"]
salon_open.rf.prev.z <- salon_open.rf.data["prev", "z value"]
salon_open.rf.prev.df <- summary(salon_open.rf)$df[2]
salon_open.rf.prev.p <- salon_open.rf.data["prev", "Pr(>|z|)"]
salon_open.rf.prev.or <- exp(salon_open.rf.prev.b)

confint(salon_open.rf)
```

### Likelihood of Moving Forward with Marketplace Activity in the Next 14 Days

```{r foodest_plan}
foodest_plan.rf <- glm(foodest_plan.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                       data = foodest, family = "binomial")
summary(foodest_plan.rf)
foodest_plan.rf.data <- summary(foodest_plan.rf)$coefficients

foodest_plan.rf.prom.b <- foodest_plan.rf.data["prom", "Estimate"]
foodest_plan.rf.prom.se <- foodest_plan.rf.data["prom", "Std. Error"]
foodest_plan.rf.prom.z <- foodest_plan.rf.data["prom", "z value"]
foodest_plan.rf.prom.df <- summary(foodest_plan.rf)$df[2]
foodest_plan.rf.prom.p <- foodest_plan.rf.data["prom", "Pr(>|z|)"]
foodest_plan.rf.prom.or <- exp(foodest_plan.rf.prom.b)

foodest_plan.rf.prev.b <- foodest_plan.rf.data["prev", "Estimate"]
foodest_plan.rf.prev.se <- foodest_plan.rf.data["prev", "Std. Error"]
foodest_plan.rf.prev.z <- foodest_plan.rf.data["prev", "z value"]
foodest_plan.rf.prev.df <- summary(foodest_plan.rf)$df[2]
foodest_plan.rf.prev.p <- foodest_plan.rf.data["prev", "Pr(>|z|)"]
foodest_plan.rf.prev.or <- exp(foodest_plan.rf.prev.b)

confint(foodest_plan.rf)
```

```{r salon_plan}
salon_plan.rf <- glm(salon_plan.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                     data = salon, family = "binomial")
summary(salon_plan.rf)
salon_plan.rf.data <- summary(salon_plan.rf)$coefficients

salon_plan.rf.prom.b <- salon_plan.rf.data["prom", "Estimate"]
salon_plan.rf.prom.se <- salon_plan.rf.data["prom", "Std. Error"]
salon_plan.rf.prom.z <- salon_plan.rf.data["prom", "z value"]
salon_plan.rf.prom.df <- summary(salon_plan.rf)$df[2]
salon_plan.rf.prom.p <- salon_plan.rf.data["prom", "Pr(>|z|)"]
salon_plan.rf.prom.or <- exp(salon_plan.rf.prom.b)

salon_plan.rf.prev.b <- salon_plan.rf.data["prev", "Estimate"]
salon_plan.rf.prev.se <- salon_plan.rf.data["prev", "Std. Error"]
salon_plan.rf.prev.z <- salon_plan.rf.data["prev", "z value"]
salon_plan.rf.prev.df <- summary(salon_plan.rf)$df[2]
salon_plan.rf.prev.p <- salon_plan.rf.data["prev", "Pr(>|z|)"]
salon_plan.rf.prev.or <- exp(salon_plan.rf.prev.b)

confint(salon_plan.rf)
```

### Behavior Involving Moving Forward with Marketplace Activity in the Past 14 Days

```{r foodest_been}
foodest_been.rf <- glm(foodest_been.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                       data = foodest, family = "binomial")
summary(foodest_been.rf)
foodest_been.rf.data <- summary(foodest_been.rf)$coefficients

foodest_been.rf.prom.b <- foodest_been.rf.data["prom", "Estimate"]
foodest_been.rf.prom.se <- foodest_been.rf.data["prom", "Std. Error"]
foodest_been.rf.prom.z <- foodest_been.rf.data["prom", "z value"]
foodest_been.rf.prom.df <- summary(foodest_been.rf)$df[2]
foodest_been.rf.prom.p <- foodest_been.rf.data["prom", "Pr(>|z|)"]
foodest_been.rf.prom.or <- exp(foodest_been.rf.prom.b)

foodest_been.rf.prev.b <- foodest_been.rf.data["prev", "Estimate"]
foodest_been.rf.prev.se <- foodest_been.rf.data["prev", "Std. Error"]
foodest_been.rf.prev.z <- foodest_been.rf.data["prev", "z value"]
foodest_been.rf.prev.df <- summary(foodest_been.rf)$df[2]
foodest_been.rf.prev.p <- foodest_been.rf.data["prev", "Pr(>|z|)"]
foodest_been.rf.prev.or <- exp(foodest_been.rf.prev.b)

confint(foodest_been.rf)
```

```{r salon_been}
salon_been.rf <- glm(salon_been.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                     data = salon, family = "binomial")
summary(salon_been.rf)
salon_been.rf.data <- summary(salon_been.rf)$coefficients

salon_been.rf.prom.b <- salon_been.rf.data["prom", "Estimate"]
salon_been.rf.prom.se <- salon_been.rf.data["prom", "Std. Error"]
salon_been.rf.prom.z <- salon_been.rf.data["prom", "z value"]
salon_been.rf.prom.df <- summary(salon_been.rf)$df[2]
salon_been.rf.prom.p <- salon_been.rf.data["prom", "Pr(>|z|)"]
salon_been.rf.prom.or <- exp(salon_been.rf.prom.b)

salon_been.rf.prev.b <- salon_been.rf.data["prev", "Estimate"]
salon_been.rf.prev.se <- salon_been.rf.data["prev", "Std. Error"]
salon_been.rf.prev.z <- salon_been.rf.data["prev", "z value"]
salon_been.rf.prev.df <- summary(salon_been.rf)$df[2]
salon_been.rf.prev.p <- salon_been.rf.data["prev", "Pr(>|z|)"]
salon_been.rf.prev.or <- exp(salon_been.rf.prev.b)

confint(salon_been.rf)
```

### Usage of Vitamin Supplements for Health and Well-Being

```{r vitamins_current}
vitamins_current.rf <- glm(vitamins_current.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                           data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")), family = "binomial")
summary(vitamins_current.rf)
vitamins_current.rf.data <- summary(vitamins_current.rf)$coefficients

vitamins_current.rf.prom.b <- vitamins_current.rf.data["prom", "Estimate"]
vitamins_current.rf.prom.se <- vitamins_current.rf.data["prom", "Std. Error"]
vitamins_current.rf.prom.z <- vitamins_current.rf.data["prom", "z value"]
vitamins_current.rf.prom.df <- summary(vitamins_current.rf)$df[2]
vitamins_current.rf.prom.p <- vitamins_current.rf.data["prom", "Pr(>|z|)"]
vitamins_current.rf.prom.or <- exp(vitamins_current.rf.prom.b)

vitamins_current.rf.prev.b <- vitamins_current.rf.data["prev", "Estimate"]
vitamins_current.rf.prev.se <- vitamins_current.rf.data["prev", "Std. Error"]
vitamins_current.rf.prev.z <- vitamins_current.rf.data["prev", "z value"]
vitamins_current.rf.prev.df <- summary(vitamins_current.rf)$df[2]
vitamins_current.rf.prev.p <- vitamins_current.rf.data["prev", "Pr(>|z|)"]
vitamins_current.rf.prev.or <- exp(vitamins_current.rf.prev.b)

confint(vitamins_current.rf)
```

### Purchases Frozen Food

```{r frozenfood}
frozenfood.rf <- glm(frozenfood.d ~ prom + prev + agegroup.num.c + pol_orient.num.c,
                     data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "Jun")), family = "binomial")
summary(frozenfood.rf)
confint(frozenfood.rf)
```

# Study 2 Results

## Differences in Regulatory Focus Before Versus After Start of Covid-19 Pandemic

```{r s2_prom_diff}
prom.covid <- lm(prom ~ covid.d + agegroup.num.c + pol_orient.num.c, data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "July")))
summary(prom.covid)
prom.covid.data <- summary(prom.covid)$coefficients

prom.covid.b <- prom.covid.data["covid.d", "Estimate"]
prom.covid.se <- prom.covid.data["covid.d", "Std. Error"]
prom.covid.t <- prom.covid.data["covid.d", "t value"]
prom.covid.df <- summary(prom.covid)$df[2]
prom.covid.p <- prom.covid.data["covid.d", "Pr(>|t|)"]

confint(prom.covid)
```

```{r s2_prev_diff}
prev.covid <- lm(prev ~ covid.d + agegroup.num.c + pol_orient.num.c, data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "July")))
summary(prev.covid)
prev.covid.data <- summary(prev.covid)$coefficients

prev.covid.b <- prev.covid.data["covid.d", "Estimate"]
prev.covid.se <- prev.covid.data["covid.d", "Std. Error"]
prev.covid.t <- prev.covid.data["covid.d", "t value"]
prev.covid.df <- summary(prev.covid)$df[2]
prev.covid.p <- prev.covid.data["covid.d", "Pr(>|t|)"]

confint(prev.covid)
```

```{r s2_aim1_plots}
# Determining pre- vs. post-Covid predictions at typical 
# levels of age group and political orientation
pred <- data.frame(
  covidF = c("Pre-Covid", "Post-Covid"),
  covid.d = c(0, 1),
  agegroup.num.c = 0,
  pol_orient.num.c = 0)
prompred <- cbind(pred, predict(prom.covid, pred, se.fit = TRUE))
prevpred <- cbind(pred, predict(prev.covid, pred, se.fit = TRUE))

promplot <- ggplot(data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "July")), aes(x = covidF, y = prom)) +
  geom_point(alpha = .15, color = "seagreen3", 
             position = position_jitter(height = .05, width = .2)) +
  geom_point(data = prompred, aes(x = covidF, y = fit), color = "black", size = 1.5) +
  geom_errorbar(data = prompred, aes(x = covidF, y = fit, ymin = fit - se.fit, ymax = fit + se.fit),
                width = .4, color = "black", size = .4) +
  geom_signif(y_position = c(4.2), xmin = c(1), xmax = c(2), annotation = c("***"),
              textsize = 6, color = "black", vjust = -.4) +
  scale_y_continuous(limits = c(1, 5)) +
  annotate("text", x = .6, y = 1.5, label = "a", size = 9) +
  labs(x = "Pre- Versus Post-Covid-19", y = "Promotion Pride")

prevplot <- ggplot(data = filter(rf, covid == "Pre-Covid" | (covid == "Post-Covid" & month == "July")), aes(x = covidF, y = prev)) +
  geom_point(alpha = .15, color = "lightcoral",
             position = position_jitter(height = .05, width = .2)) +
  geom_point(data = prevpred, aes(x = covidF, y = fit), color = "black", size = 1.5) +
  geom_errorbar(data = prevpred, aes(x = covidF, y = fit, ymin = fit - se.fit, ymax = fit + se.fit),
                width = .4, color = "black", size = .4) +
  geom_signif(y_position = c(4.2), xmin = c(1), xmax = c(2), annotation = c("***"),
              textsize = 6, color = "black", vjust = -.4) +
  scale_y_continuous(limits = c(1, 5)) +
  annotate("text", x = .6, y = 1.5, label = "b", size = 9) +
  labs(x = "Pre- Versus Post-Covid-19", y = "Prevention Pride")
```

Figure 2: Model-predicted differences in promotion pride and prevention pride before versus after the start of the Covid-19 pandemic at typical levels of age group and political ideology. Error bars represent standard errors of the mean.

```{r fig2, include = TRUE, fig.align = "center"}
grid.arrange(promplot, prevplot, ncol=2, heights = c(3, 3), widths = c(4, 4))
```

### Monthly Analysis

```{r s1s2_prom_diff_age_pol}
prom.month <- lm(prom ~ month.num + agegroup.num.c + pol_orient.num.c, data = rf)
summary(prom.month)
prom.month.data <- summary(prom.month)$coefficients

prom.month.b <- prom.month.data["month.num", "Estimate"]
prom.month.se <- prom.month.data["month.num", "Std. Error"]
prom.month.t <- prom.month.data["month.num", "t value"]
prom.month.numf <- summary(prom.month)$df[2]
prom.month.p <- prom.month.data["month.num", "Pr(>|t|)"]

confint(prom.month)
```

```{r s1s2_prev_diff_age_pol}
prev.month <- lm(prev ~ month.num + agegroup.num.c + pol_orient.num.c, data = rf)
summary(prev.month)
prev.month.data <- summary(prev.month)$coefficients

prev.month.b <- prev.month.data["month.num", "Estimate"]
prev.month.se <- prev.month.data["month.num", "Std. Error"]
prev.month.t <- prev.month.data["month.num", "t value"]
prev.month.numf <- summary(prev.month)$df[2]
prev.month.p <- prev.month.data["month.num", "Pr(>|t|)"]

confint(prev.month)
```

## Associations Between Post-Covid-19 Regulatory Focus Pride and Behavioral Outcomes

### Intentions and Behavior Regarding Marketplace Activity

#### Moving Forward with Marketplace Activity in the Past 14 Days: Entertainment Activities

```{r out_restaurant}
out_restaurant.rf <- glm(out_restaurant.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(out_restaurant.rf)
out_restaurant.rf.data <- summary(out_restaurant.rf)$coefficients

out_restaurant.rf.prom.b <- out_restaurant.rf.data["prom", "Estimate"]
out_restaurant.rf.prom.se <- out_restaurant.rf.data["prom", "Std. Error"]
out_restaurant.rf.prom.z <- out_restaurant.rf.data["prom", "z value"]
out_restaurant.rf.prom.df <- summary(out_restaurant.rf)$df[2]
out_restaurant.rf.prom.p <- out_restaurant.rf.data["prom", "Pr(>|z|)"]
out_restaurant.rf.prom.or <- exp(out_restaurant.rf.prom.b)

out_restaurant.rf.prev.b <- out_restaurant.rf.data["prev", "Estimate"]
out_restaurant.rf.prev.se <- out_restaurant.rf.data["prev", "Std. Error"]
out_restaurant.rf.prev.z <- out_restaurant.rf.data["prev", "z value"]
out_restaurant.rf.prev.df <- summary(out_restaurant.rf)$df[2]
out_restaurant.rf.prev.p <- out_restaurant.rf.data["prev", "Pr(>|z|)"]
out_restaurant.rf.prev.or <- exp(out_restaurant.rf.prev.b)

confint(out_restaurant.rf)
```

```{r out_publicevent}
out_publicevent.rf <- glm(out_publicevent.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(out_publicevent.rf)
out_publicevent.rf.data <- summary(out_publicevent.rf)$coefficients

out_publicevent.rf.prom.b <- out_publicevent.rf.data["prom", "Estimate"]
out_publicevent.rf.prom.se <- out_publicevent.rf.data["prom", "Std. Error"]
out_publicevent.rf.prom.z <- out_publicevent.rf.data["prom", "z value"]
out_publicevent.rf.prom.df <- summary(out_publicevent.rf)$df[2]
out_publicevent.rf.prom.p <- out_publicevent.rf.data["prom", "Pr(>|z|)"]
out_publicevent.rf.prom.or <- exp(out_publicevent.rf.prom.b)

out_publicevent.rf.prev.b <- out_publicevent.rf.data["prev", "Estimate"]
out_publicevent.rf.prev.se <- out_publicevent.rf.data["prev", "Std. Error"]
out_publicevent.rf.prev.z <- out_publicevent.rf.data["prev", "z value"]
out_publicevent.rf.prev.df <- summary(out_publicevent.rf)$df[2]
out_publicevent.rf.prev.p <- out_publicevent.rf.data["prev", "Pr(>|z|)"]
out_publicevent.rf.prev.or <- exp(out_publicevent.rf.prev.b)

confint(out_publicevent.rf)
```

```{r out_bar}
out_bar.rf <- glm(out_bar.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(out_bar.rf)
out_bar.rf.data <- summary(out_bar.rf)$coefficients

out_bar.rf.prom.b <- out_bar.rf.data["prom", "Estimate"]
out_bar.rf.prom.se <- out_bar.rf.data["prom", "Std. Error"]
out_bar.rf.prom.z <- out_bar.rf.data["prom", "z value"]
out_bar.rf.prom.df <- summary(out_bar.rf)$df[2]
out_bar.rf.prom.p <- out_bar.rf.data["prom", "Pr(>|z|)"]
out_bar.rf.prom.or <- exp(out_bar.rf.prom.b)

out_bar.rf.prev.b <- out_bar.rf.data["prev", "Estimate"]
out_bar.rf.prev.se <- out_bar.rf.data["prev", "Std. Error"]
out_bar.rf.prev.z <- out_bar.rf.data["prev", "z value"]
out_bar.rf.prev.df <- summary(out_bar.rf)$df[2]
out_bar.rf.prev.p <- out_bar.rf.data["prev", "Pr(>|z|)"]
out_bar.rf.prev.or <- exp(out_bar.rf.prev.b)

confint(out_bar.rf)
```

#### Moving Forward with Marketplace Activity in the Past 14 Days: Shopping Activities

```{r shop_mall}
shop_mall.rf <- glm(shop_mall.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(shop_mall.rf)
shop_mall.rf.data <- summary(shop_mall.rf)$coefficients

shop_mall.rf.prom.b <- shop_mall.rf.data["prom", "Estimate"]
shop_mall.rf.prom.se <- shop_mall.rf.data["prom", "Std. Error"]
shop_mall.rf.prom.z <- shop_mall.rf.data["prom", "z value"]
shop_mall.rf.prom.df <- summary(shop_mall.rf)$df[2]
shop_mall.rf.prom.p <- shop_mall.rf.data["prom", "Pr(>|z|)"]
shop_mall.rf.prom.or <- exp(shop_mall.rf.prom.b)

shop_mall.rf.prev.b <- shop_mall.rf.data["prev", "Estimate"]
shop_mall.rf.prev.se <- shop_mall.rf.data["prev", "Std. Error"]
shop_mall.rf.prev.z <- shop_mall.rf.data["prev", "z value"]
shop_mall.rf.prev.df <- summary(shop_mall.rf)$df[2]
shop_mall.rf.prev.p <- shop_mall.rf.data["prev", "Pr(>|z|)"]
shop_mall.rf.prev.or <- exp(shop_mall.rf.prev.b)

confint(shop_mall.rf)
```

```{r shop_grocery}
shop_grocery.rf <- glm(shop_grocery.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(shop_grocery.rf)
shop_grocery.rf.data <- summary(shop_grocery.rf)$coefficients

shop_grocery.rf.prom.b <- shop_grocery.rf.data["prom", "Estimate"]
shop_grocery.rf.prom.se <- shop_grocery.rf.data["prom", "Std. Error"]
shop_grocery.rf.prom.z <- shop_grocery.rf.data["prom", "z value"]
shop_grocery.rf.prom.df <- summary(shop_grocery.rf)$df[2]
shop_grocery.rf.prom.p <- shop_grocery.rf.data["prom", "Pr(>|z|)"]
shop_grocery.rf.prom.or <- exp(shop_grocery.rf.prom.b)

shop_grocery.rf.prev.b <- shop_grocery.rf.data["prev", "Estimate"]
shop_grocery.rf.prev.se <- shop_grocery.rf.data["prev", "Std. Error"]
shop_grocery.rf.prev.z <- shop_grocery.rf.data["prev", "z value"]
shop_grocery.rf.prev.df <- summary(shop_grocery.rf)$df[2]
shop_grocery.rf.prev.p <- shop_grocery.rf.data["prev", "Pr(>|z|)"]
shop_grocery.rf.prev.or <- exp(shop_grocery.rf.prev.b)

confint(shop_grocery.rf)
```

```{r order_grocery_delivery}
order_grocery_delivery.rf <- glm(order_grocery_delivery.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(order_grocery_delivery.rf)
order_grocery_delivery.rf.data <- summary(order_grocery_delivery.rf)$coefficients

order_grocery_delivery.rf.prom.b <- order_grocery_delivery.rf.data["prom", "Estimate"]
order_grocery_delivery.rf.prom.se <- order_grocery_delivery.rf.data["prom", "Std. Error"]
order_grocery_delivery.rf.prom.z <- order_grocery_delivery.rf.data["prom", "z value"]
order_grocery_delivery.rf.prom.df <- summary(order_grocery_delivery.rf)$df[2]
order_grocery_delivery.rf.prom.p <- order_grocery_delivery.rf.data["prom", "Pr(>|z|)"]
order_grocery_delivery.rf.prom.or <- exp(order_grocery_delivery.rf.prom.b)

order_grocery_delivery.rf.prev.b <- order_grocery_delivery.rf.data["prev", "Estimate"]
order_grocery_delivery.rf.prev.se <- order_grocery_delivery.rf.data["prev", "Std. Error"]
order_grocery_delivery.rf.prev.z <- order_grocery_delivery.rf.data["prev", "z value"]
order_grocery_delivery.rf.prev.df <- summary(order_grocery_delivery.rf)$df[2]
order_grocery_delivery.rf.prev.p <- order_grocery_delivery.rf.data["prev", "Pr(>|z|)"]
order_grocery_delivery.rf.prev.or <- exp(order_grocery_delivery.rf.prev.b)

confint(order_grocery_delivery.rf)
```

```{r order_grocery_pickup}
order_grocery_pickup.rf <- glm(order_grocery_pickup.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(order_grocery_pickup.rf)
order_grocery_pickup.rf.data <- summary(order_grocery_pickup.rf)$coefficients

order_grocery_pickup.rf.prom.b <- order_grocery_pickup.rf.data["prom", "Estimate"]
order_grocery_pickup.rf.prom.se <- order_grocery_pickup.rf.data["prom", "Std. Error"]
order_grocery_pickup.rf.prom.z <- order_grocery_pickup.rf.data["prom", "z value"]
order_grocery_pickup.rf.prom.df <- summary(order_grocery_pickup.rf)$df[2]
order_grocery_pickup.rf.prom.p <- order_grocery_pickup.rf.data["prom", "Pr(>|z|)"]
order_grocery_pickup.rf.prom.or <- exp(order_grocery_pickup.rf.prom.b)

order_grocery_pickup.rf.prev.b <- order_grocery_pickup.rf.data["prev", "Estimate"]
order_grocery_pickup.rf.prev.se <- order_grocery_pickup.rf.data["prev", "Std. Error"]
order_grocery_pickup.rf.prev.z <- order_grocery_pickup.rf.data["prev", "z value"]
order_grocery_pickup.rf.prev.df <- summary(order_grocery_pickup.rf)$df[2]
order_grocery_pickup.rf.prev.p <- order_grocery_pickup.rf.data["prev", "Pr(>|z|)"]
order_grocery_pickup.rf.prev.or <- exp(order_grocery_pickup.rf.prev.b)

confint(order_grocery_pickup.rf)
```

#### Moving Forward with Marketplace Activity in the Past 14 Days: Transportation Activities

```{r travel_car}
travel_car.rf <- glm(travel_car.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(travel_car.rf)
travel_car.rf.data <- summary(travel_car.rf)$coefficients

travel_car.rf.prom.b <- travel_car.rf.data["prom", "Estimate"]
travel_car.rf.prom.se <- travel_car.rf.data["prom", "Std. Error"]
travel_car.rf.prom.z <- travel_car.rf.data["prom", "z value"]
travel_car.rf.prom.df <- summary(travel_car.rf)$df[2]
travel_car.rf.prom.p <- travel_car.rf.data["prom", "Pr(>|z|)"]
travel_car.rf.prom.or <- exp(travel_car.rf.prom.b)

travel_car.rf.prev.b <- travel_car.rf.data["prev", "Estimate"]
travel_car.rf.prev.se <- travel_car.rf.data["prev", "Std. Error"]
travel_car.rf.prev.z <- travel_car.rf.data["prev", "z value"]
travel_car.rf.prev.df <- summary(travel_car.rf)$df[2]
travel_car.rf.prev.p <- travel_car.rf.data["prev", "Pr(>|z|)"]
travel_car.rf.prev.or <- exp(travel_car.rf.prev.b)

confint(travel_car.rf)
```

```{r travel_air}
travel_air.rf <- glm(travel_air.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(travel_air.rf)
travel_air.rf.data <- summary(travel_air.rf)$coefficients

travel_air.rf.prom.b <- travel_air.rf.data["prom", "Estimate"]
travel_air.rf.prom.se <- travel_air.rf.data["prom", "Std. Error"]
travel_air.rf.prom.z <- travel_air.rf.data["prom", "z value"]
travel_air.rf.prom.df <- summary(travel_air.rf)$df[2]
travel_air.rf.prom.p <- travel_air.rf.data["prom", "Pr(>|z|)"]
travel_air.rf.prom.or <- exp(travel_air.rf.prom.b)

travel_air.rf.prev.b <- travel_air.rf.data["prev", "Estimate"]
travel_air.rf.prev.se <- travel_air.rf.data["prev", "Std. Error"]
travel_air.rf.prev.z <- travel_air.rf.data["prev", "z value"]
travel_air.rf.prev.df <- summary(travel_air.rf)$df[2]
travel_air.rf.prev.p <- travel_air.rf.data["prev", "Pr(>|z|)"]
travel_air.rf.prev.or <- exp(travel_air.rf.prev.b)

confint(travel_air.rf)
```

```{r travel_rideshare}
travel_rideshare.rf <- glm(travel_rideshare.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(travel_rideshare.rf)
travel_rideshare.rf.data <- summary(travel_rideshare.rf)$coefficients

travel_rideshare.rf.prom.b <- travel_rideshare.rf.data["prom", "Estimate"]
travel_rideshare.rf.prom.se <- travel_rideshare.rf.data["prom", "Std. Error"]
travel_rideshare.rf.prom.z <- travel_rideshare.rf.data["prom", "z value"]
travel_rideshare.rf.prom.df <- summary(travel_rideshare.rf)$df[2]
travel_rideshare.rf.prom.p <- travel_rideshare.rf.data["prom", "Pr(>|z|)"]
travel_rideshare.rf.prom.or <- exp(travel_rideshare.rf.prom.b)

travel_rideshare.rf.prev.b <- travel_rideshare.rf.data["prev", "Estimate"]
travel_rideshare.rf.prev.se <- travel_rideshare.rf.data["prev", "Std. Error"]
travel_rideshare.rf.prev.z <- travel_rideshare.rf.data["prev", "z value"]
travel_rideshare.rf.prev.df <- summary(travel_rideshare.rf)$df[2]
travel_rideshare.rf.prev.p <- travel_rideshare.rf.data["prev", "Pr(>|z|)"]
travel_rideshare.rf.prev.or <- exp(travel_rideshare.rf.prev.b)

confint(travel_rideshare.rf)
```

```{r travel_taxi}
travel_taxi.rf <- glm(travel_taxi.d ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf, family = "binomial")
summary(travel_taxi.rf)
travel_taxi.rf.data <- summary(travel_taxi.rf)$coefficients

travel_taxi.rf.prom.b <- travel_taxi.rf.data["prom", "Estimate"]
travel_taxi.rf.prom.se <- travel_taxi.rf.data["prom", "Std. Error"]
travel_taxi.rf.prom.z <- travel_taxi.rf.data["prom", "z value"]
travel_taxi.rf.prom.df <- summary(travel_taxi.rf)$df[2]
travel_taxi.rf.prom.p <- travel_taxi.rf.data["prom", "Pr(>|z|)"]
travel_taxi.rf.prom.or <- exp(travel_taxi.rf.prom.b)

travel_taxi.rf.prev.b <- travel_taxi.rf.data["prev", "Estimate"]
travel_taxi.rf.prev.se <- travel_taxi.rf.data["prev", "Std. Error"]
travel_taxi.rf.prev.z <- travel_taxi.rf.data["prev", "z value"]
travel_taxi.rf.prev.df <- summary(travel_taxi.rf)$df[2]
travel_taxi.rf.prev.p <- travel_taxi.rf.data["prev", "Pr(>|z|)"]
travel_taxi.rf.prev.or <- exp(travel_taxi.rf.prev.b)

confint(travel_taxi.rf)
```

#### Likelihood of Moving Forward with Marketplace Activity in the Next 14 Days: Entertainment Activities

```{r out_restaurant_l}
out_restaurant.rf <- lm(out_restaurant_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(out_restaurant.rf)
out_restaurant.rf.data <- summary(out_restaurant.rf)$coefficients

out_restaurant.rf.prom.b <- out_restaurant.rf.data["prom", "Estimate"]
out_restaurant.rf.prom.se <- out_restaurant.rf.data["prom", "Std. Error"]
out_restaurant.rf.prom.t <- out_restaurant.rf.data["prom", "t value"]
out_restaurant.rf.prom.df <- round(summary(out_restaurant.rf)$df[2], digits = 0)
out_restaurant.rf.prom.p <- out_restaurant.rf.data["prom", "Pr(>|t|)"]
out_restaurant.rf.prom.or <- exp(out_restaurant.rf.prom.b)

out_restaurant.rf.prev.b <- out_restaurant.rf.data["prev", "Estimate"]
out_restaurant.rf.prev.se <- out_restaurant.rf.data["prev", "Std. Error"]
out_restaurant.rf.prev.t <- out_restaurant.rf.data["prev", "t value"]
out_restaurant.rf.prev.df <- round(summary(out_restaurant.rf)$df[2], digits = 0)
out_restaurant.rf.prev.p <- out_restaurant.rf.data["prev", "Pr(>|t|)"]
out_restaurant.rf.prev.or <- exp(out_restaurant.rf.prev.b)

confint(out_restaurant.rf)
```

```{r out_publicevent_l}
out_publicevent.rf <- lm(out_publicevent_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(out_publicevent.rf)
out_publicevent.rf.data <- summary(out_publicevent.rf)$coefficients

out_publicevent.rf.prom.b <- out_publicevent.rf.data["prom", "Estimate"]
out_publicevent.rf.prom.se <- out_publicevent.rf.data["prom", "Std. Error"]
out_publicevent.rf.prom.t <- out_publicevent.rf.data["prom", "t value"]
out_publicevent.rf.prom.df <- round(summary(out_publicevent.rf)$df[2], digits = 0)
out_publicevent.rf.prom.p <- out_publicevent.rf.data["prom", "Pr(>|t|)"]
out_publicevent.rf.prom.or <- exp(out_publicevent.rf.prom.b)

out_publicevent.rf.prev.b <- out_publicevent.rf.data["prev", "Estimate"]
out_publicevent.rf.prev.se <- out_publicevent.rf.data["prev", "Std. Error"]
out_publicevent.rf.prev.t <- out_publicevent.rf.data["prev", "t value"]
out_publicevent.rf.prev.df <- round(summary(out_publicevent.rf)$df[2], digits = 0)
out_publicevent.rf.prev.p <- out_publicevent.rf.data["prev", "Pr(>|t|)"]
out_publicevent.rf.prev.or <- exp(out_publicevent.rf.prev.b)

confint(out_publicevent.rf)
```

```{r out_bar_l}
out_bar.rf <- lm(out_bar_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(out_bar.rf)
out_bar.rf.data <- summary(out_bar.rf)$coefficients

out_bar.rf.prom.b <- out_bar.rf.data["prom", "Estimate"]
out_bar.rf.prom.se <- out_bar.rf.data["prom", "Std. Error"]
out_bar.rf.prom.t <- out_bar.rf.data["prom", "t value"]
out_bar.rf.prom.df <- round(summary(out_bar.rf)$df[2], digits = 0)
out_bar.rf.prom.p <- out_bar.rf.data["prom", "Pr(>|t|)"]
out_bar.rf.prom.or <- exp(out_bar.rf.prom.b)

out_bar.rf.prev.b <- out_bar.rf.data["prev", "Estimate"]
out_bar.rf.prev.se <- out_bar.rf.data["prev", "Std. Error"]
out_bar.rf.prev.t <- out_bar.rf.data["prev", "t value"]
out_bar.rf.prev.df <- round(summary(out_bar.rf)$df[2], digits = 0)
out_bar.rf.prev.p <- out_bar.rf.data["prev", "Pr(>|t|)"]
out_bar.rf.prev.or <- exp(out_bar.rf.prev.b)

confint(out_bar.rf)
```

#### Likelihood of Moving Forward with Marketplace Activity in the Next 14 Days: Shopping Activities

```{r shop_mall_l}
shop_mall.rf <- lm(shop_mall_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(shop_mall.rf)
shop_mall.rf.data <- summary(shop_mall.rf)$coefficients

shop_mall.rf.prom.b <- shop_mall.rf.data["prom", "Estimate"]
shop_mall.rf.prom.se <- shop_mall.rf.data["prom", "Std. Error"]
shop_mall.rf.prom.t <- shop_mall.rf.data["prom", "t value"]
shop_mall.rf.prom.df <- round(summary(shop_mall.rf)$df[2], digits = 0)
shop_mall.rf.prom.p <- shop_mall.rf.data["prom", "Pr(>|t|)"]
shop_mall.rf.prom.or <- exp(shop_mall.rf.prom.b)

shop_mall.rf.prev.b <- shop_mall.rf.data["prev", "Estimate"]
shop_mall.rf.prev.se <- shop_mall.rf.data["prev", "Std. Error"]
shop_mall.rf.prev.t <- shop_mall.rf.data["prev", "t value"]
shop_mall.rf.prev.df <- round(summary(shop_mall.rf)$df[2], digits = 0)
shop_mall.rf.prev.p <- shop_mall.rf.data["prev", "Pr(>|t|)"]
shop_mall.rf.prev.or <- exp(shop_mall.rf.prev.b)

confint(shop_mall.rf)
```

```{r shop_grocery_l}
shop_grocery.rf <- lm(shop_grocery_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(shop_grocery.rf)
shop_grocery.rf.data <- summary(shop_grocery.rf)$coefficients

shop_grocery.rf.prom.b <- shop_grocery.rf.data["prom", "Estimate"]
shop_grocery.rf.prom.se <- shop_grocery.rf.data["prom", "Std. Error"]
shop_grocery.rf.prom.t <- shop_grocery.rf.data["prom", "t value"]
shop_grocery.rf.prom.df <- round(summary(shop_grocery.rf)$df[2], digits = 0)
shop_grocery.rf.prom.p <- shop_grocery.rf.data["prom", "Pr(>|t|)"]
shop_grocery.rf.prom.or <- exp(shop_grocery.rf.prom.b)

shop_grocery.rf.prev.b <- shop_grocery.rf.data["prev", "Estimate"]
shop_grocery.rf.prev.se <- shop_grocery.rf.data["prev", "Std. Error"]
shop_grocery.rf.prev.t <- shop_grocery.rf.data["prev", "t value"]
shop_grocery.rf.prev.df <- round(summary(shop_grocery.rf)$df[2], digits = 0)
shop_grocery.rf.prev.p <- shop_grocery.rf.data["prev", "Pr(>|t|)"]
shop_grocery.rf.prev.or <- exp(shop_grocery.rf.prev.b)

confint(shop_grocery.rf)
```

```{r order_grocery_delivery_l}
order_grocery_delivery.rf <- lm(order_grocery_delivery_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(order_grocery_delivery.rf)
order_grocery_delivery.rf.data <- summary(order_grocery_delivery.rf)$coefficients

order_grocery_delivery.rf.prom.b <- order_grocery_delivery.rf.data["prom", "Estimate"]
order_grocery_delivery.rf.prom.se <- order_grocery_delivery.rf.data["prom", "Std. Error"]
order_grocery_delivery.rf.prom.t <- order_grocery_delivery.rf.data["prom", "t value"]
order_grocery_delivery.rf.prom.df <- round(summary(order_grocery_delivery.rf)$df[2], digits = 0)
order_grocery_delivery.rf.prom.p <- order_grocery_delivery.rf.data["prom", "Pr(>|t|)"]
order_grocery_delivery.rf.prom.or <- exp(order_grocery_delivery.rf.prom.b)

order_grocery_delivery.rf.prev.b <- order_grocery_delivery.rf.data["prev", "Estimate"]
order_grocery_delivery.rf.prev.se <- order_grocery_delivery.rf.data["prev", "Std. Error"]
order_grocery_delivery.rf.prev.t <- order_grocery_delivery.rf.data["prev", "t value"]
order_grocery_delivery.rf.prev.df <- round(summary(order_grocery_delivery.rf)$df[2], digits = 0)
order_grocery_delivery.rf.prev.p <- order_grocery_delivery.rf.data["prev", "Pr(>|t|)"]
order_grocery_delivery.rf.prev.or <- exp(order_grocery_delivery.rf.prev.b)

confint(order_grocery_delivery.rf)
```

```{r order_grocery_pickup_l}
order_grocery_pickup.rf <- lm(order_grocery_pickup_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(order_grocery_pickup.rf)
order_grocery_pickup.rf.data <- summary(order_grocery_pickup.rf)$coefficients

order_grocery_pickup.rf.prom.b <- order_grocery_pickup.rf.data["prom", "Estimate"]
order_grocery_pickup.rf.prom.se <- order_grocery_pickup.rf.data["prom", "Std. Error"]
order_grocery_pickup.rf.prom.t <- order_grocery_pickup.rf.data["prom", "t value"]
order_grocery_pickup.rf.prom.df <- round(summary(order_grocery_pickup.rf)$df[2], digits = 0)
order_grocery_pickup.rf.prom.p <- order_grocery_pickup.rf.data["prom", "Pr(>|t|)"]
order_grocery_pickup.rf.prom.or <- exp(order_grocery_pickup.rf.prom.b)

order_grocery_pickup.rf.prev.b <- order_grocery_pickup.rf.data["prev", "Estimate"]
order_grocery_pickup.rf.prev.se <- order_grocery_pickup.rf.data["prev", "Std. Error"]
order_grocery_pickup.rf.prev.t <- order_grocery_pickup.rf.data["prev", "t value"]
order_grocery_pickup.rf.prev.df <- round(summary(order_grocery_pickup.rf)$df[2], digits = 0)
order_grocery_pickup.rf.prev.p <- order_grocery_pickup.rf.data["prev", "Pr(>|t|)"]
order_grocery_pickup.rf.prev.or <- exp(order_grocery_pickup.rf.prev.b)

confint(order_grocery_pickup.rf)
```

#### Likelihood of Moving Forward with Marketplace Activity in the Next 14 Days: Transportation Activities

```{r travel_car_l}
travel_car.rf <- lm(travel_car_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(travel_car.rf)
travel_car.rf.data <- summary(travel_car.rf)$coefficients

travel_car.rf.prom.b <- travel_car.rf.data["prom", "Estimate"]
travel_car.rf.prom.se <- travel_car.rf.data["prom", "Std. Error"]
travel_car.rf.prom.t <- travel_car.rf.data["prom", "t value"]
travel_car.rf.prom.df <- round(summary(travel_car.rf)$df[2], digits = 0)
travel_car.rf.prom.p <- travel_car.rf.data["prom", "Pr(>|t|)"]
travel_car.rf.prom.or <- exp(travel_car.rf.prom.b)

travel_car.rf.prev.b <- travel_car.rf.data["prev", "Estimate"]
travel_car.rf.prev.se <- travel_car.rf.data["prev", "Std. Error"]
travel_car.rf.prev.t <- travel_car.rf.data["prev", "t value"]
travel_car.rf.prev.df <- round(summary(travel_car.rf)$df[2], digits = 0)
travel_car.rf.prev.p <- travel_car.rf.data["prev", "Pr(>|t|)"]
travel_car.rf.prev.or <- exp(travel_car.rf.prev.b)

confint(travel_car.rf)
```

```{r travel_air_l}
travel_air.rf <- lm(travel_air_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(travel_air.rf)
travel_air.rf.data <- summary(travel_air.rf)$coefficients

travel_air.rf.prom.b <- travel_air.rf.data["prom", "Estimate"]
travel_air.rf.prom.se <- travel_air.rf.data["prom", "Std. Error"]
travel_air.rf.prom.t <- travel_air.rf.data["prom", "t value"]
travel_air.rf.prom.df <- round(summary(travel_air.rf)$df[2], digits = 0)
travel_air.rf.prom.p <- travel_air.rf.data["prom", "Pr(>|t|)"]
travel_air.rf.prom.or <- exp(travel_air.rf.prom.b)

travel_air.rf.prev.b <- travel_air.rf.data["prev", "Estimate"]
travel_air.rf.prev.se <- travel_air.rf.data["prev", "Std. Error"]
travel_air.rf.prev.t <- travel_air.rf.data["prev", "t value"]
travel_air.rf.prev.df <- round(summary(travel_air.rf)$df[2], digits = 0)
travel_air.rf.prev.p <- travel_air.rf.data["prev", "Pr(>|t|)"]
travel_air.rf.prev.or <- exp(travel_air.rf.prev.b)

confint(travel_air.rf)
```

```{r travel_rideshare_l}
travel_rideshare.rf <- lm(travel_rideshare_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(travel_rideshare.rf)
travel_rideshare.rf.data <- summary(travel_rideshare.rf)$coefficients

travel_rideshare.rf.prom.b <- travel_rideshare.rf.data["prom", "Estimate"]
travel_rideshare.rf.prom.se <- travel_rideshare.rf.data["prom", "Std. Error"]
travel_rideshare.rf.prom.t <- travel_rideshare.rf.data["prom", "t value"]
travel_rideshare.rf.prom.df <- round(summary(travel_rideshare.rf)$df[2], digits = 0)
travel_rideshare.rf.prom.p <- travel_rideshare.rf.data["prom", "Pr(>|t|)"]
travel_rideshare.rf.prom.or <- exp(travel_rideshare.rf.prom.b)

travel_rideshare.rf.prev.b <- travel_rideshare.rf.data["prev", "Estimate"]
travel_rideshare.rf.prev.se <- travel_rideshare.rf.data["prev", "Std. Error"]
travel_rideshare.rf.prev.t <- travel_rideshare.rf.data["prev", "t value"]
travel_rideshare.rf.prev.df <- round(summary(travel_rideshare.rf)$df[2], digits = 0)
travel_rideshare.rf.prev.p <- travel_rideshare.rf.data["prev", "Pr(>|t|)"]
travel_rideshare.rf.prev.or <- exp(travel_rideshare.rf.prev.b)

confint(travel_rideshare.rf)
```

```{r travel_taxi_l}
travel_taxi.rf <- lm(travel_taxi_l ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(travel_taxi.rf)
travel_taxi.rf.data <- summary(travel_taxi.rf)$coefficients

travel_taxi.rf.prom.b <- travel_taxi.rf.data["prom", "Estimate"]
travel_taxi.rf.prom.se <- travel_taxi.rf.data["prom", "Std. Error"]
travel_taxi.rf.prom.t <- travel_taxi.rf.data["prom", "t value"]
travel_taxi.rf.prom.df <- round(summary(travel_taxi.rf)$df[2], digits = 0)
travel_taxi.rf.prom.p <- travel_taxi.rf.data["prom", "Pr(>|t|)"]
travel_taxi.rf.prom.or <- exp(travel_taxi.rf.prom.b)

travel_taxi.rf.prev.b <- travel_taxi.rf.data["prev", "Estimate"]
travel_taxi.rf.prev.se <- travel_taxi.rf.data["prev", "Std. Error"]
travel_taxi.rf.prev.t <- travel_taxi.rf.data["prev", "t value"]
travel_taxi.rf.prev.df <- round(summary(travel_taxi.rf)$df[2], digits = 0)
travel_taxi.rf.prev.p <- travel_taxi.rf.data["prev", "Pr(>|t|)"]
travel_taxi.rf.prev.or <- exp(travel_taxi.rf.prev.b)

confint(travel_taxi.rf)
```

### Engagement in Pandemic-Related Safety Behaviors

```{r wash_hands_sanitizer}
wash_hands_sanitizer.rf <- lm(wash_hands_sanitizer ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(wash_hands_sanitizer.rf)
wash_hands_sanitizer.rf.data <- summary(wash_hands_sanitizer.rf)$coefficients

wash_hands_sanitizer.rf.prom.b <- wash_hands_sanitizer.rf.data["prom", "Estimate"]
wash_hands_sanitizer.rf.prom.se <- wash_hands_sanitizer.rf.data["prom", "Std. Error"]
wash_hands_sanitizer.rf.prom.t <- wash_hands_sanitizer.rf.data["prom", "t value"]
wash_hands_sanitizer.rf.prom.df <- round(summary(wash_hands_sanitizer.rf)$df[2], digits = 0)
wash_hands_sanitizer.rf.prom.p <- wash_hands_sanitizer.rf.data["prom", "Pr(>|t|)"]
wash_hands_sanitizer.rf.prom.or <- exp(wash_hands_sanitizer.rf.prom.b)

wash_hands_sanitizer.rf.prev.b <- wash_hands_sanitizer.rf.data["prev", "Estimate"]
wash_hands_sanitizer.rf.prev.se <- wash_hands_sanitizer.rf.data["prev", "Std. Error"]
wash_hands_sanitizer.rf.prev.t <- wash_hands_sanitizer.rf.data["prev", "t value"]
wash_hands_sanitizer.rf.prev.df <- round(summary(wash_hands_sanitizer.rf)$df[2], digits = 0)
wash_hands_sanitizer.rf.prev.p <- wash_hands_sanitizer.rf.data["prev", "Pr(>|t|)"]
wash_hands_sanitizer.rf.prev.or <- exp(wash_hands_sanitizer.rf.prev.b)

confint(wash_hands_sanitizer.rf)
```

```{r wear_mask_self_family}
wear_mask_self_family.rf <- lm(wear_mask_self_family ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(wear_mask_self_family.rf)
wear_mask_self_family.rf.data <- summary(wear_mask_self_family.rf)$coefficients

wear_mask_self_family.rf.prom.b <- wear_mask_self_family.rf.data["prom", "Estimate"]
wear_mask_self_family.rf.prom.se <- wear_mask_self_family.rf.data["prom", "Std. Error"]
wear_mask_self_family.rf.prom.t <- wear_mask_self_family.rf.data["prom", "t value"]
wear_mask_self_family.rf.prom.df <- round(summary(wear_mask_self_family.rf)$df[2], digits = 0)
wear_mask_self_family.rf.prom.p <- wear_mask_self_family.rf.data["prom", "Pr(>|t|)"]
wear_mask_self_family.rf.prom.or <- exp(wear_mask_self_family.rf.prom.b)

wear_mask_self_family.rf.prev.b <- wear_mask_self_family.rf.data["prev", "Estimate"]
wear_mask_self_family.rf.prev.se <- wear_mask_self_family.rf.data["prev", "Std. Error"]
wear_mask_self_family.rf.prev.t <- wear_mask_self_family.rf.data["prev", "t value"]
wear_mask_self_family.rf.prev.df <- round(summary(wear_mask_self_family.rf)$df[2], digits = 0)
wear_mask_self_family.rf.prev.p <- wear_mask_self_family.rf.data["prev", "Pr(>|t|)"]
wear_mask_self_family.rf.prev.or <- exp(wear_mask_self_family.rf.prev.b)

confint(wear_mask_self_family.rf)
```

```{r wear_mask_others}
wear_mask_others.rf <- lm(wear_mask_others ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(wear_mask_others.rf)
wear_mask_others.rf.data <- summary(wear_mask_others.rf)$coefficients

wear_mask_others.rf.prom.b <- wear_mask_others.rf.data["prom", "Estimate"]
wear_mask_others.rf.prom.se <- wear_mask_others.rf.data["prom", "Std. Error"]
wear_mask_others.rf.prom.t <- wear_mask_others.rf.data["prom", "t value"]
wear_mask_others.rf.prom.df <- round(summary(wear_mask_others.rf)$df[2], digits = 0)
wear_mask_others.rf.prom.p <- wear_mask_others.rf.data["prom", "Pr(>|t|)"]
wear_mask_others.rf.prom.or <- exp(wear_mask_others.rf.prom.b)

wear_mask_others.rf.prev.b <- wear_mask_others.rf.data["prev", "Estimate"]
wear_mask_others.rf.prev.se <- wear_mask_others.rf.data["prev", "Std. Error"]
wear_mask_others.rf.prev.t <- wear_mask_others.rf.data["prev", "t value"]
wear_mask_others.rf.prev.df <- round(summary(wear_mask_others.rf)$df[2], digits = 0)
wear_mask_others.rf.prev.p <- wear_mask_others.rf.data["prev", "Pr(>|t|)"]
wear_mask_others.rf.prev.or <- exp(wear_mask_others.rf.prev.b)

confint(wear_mask_others.rf)
```

```{r wear_gloves}
wear_gloves.rf <- lm(wear_gloves ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(wear_gloves.rf)
wear_gloves.rf.data <- summary(wear_gloves.rf)$coefficients

wear_gloves.rf.prom.b <- wear_gloves.rf.data["prom", "Estimate"]
wear_gloves.rf.prom.se <- wear_gloves.rf.data["prom", "Std. Error"]
wear_gloves.rf.prom.t <- wear_gloves.rf.data["prom", "t value"]
wear_gloves.rf.prom.df <- round(summary(wear_gloves.rf)$df[2], digits = 0)
wear_gloves.rf.prom.p <- wear_gloves.rf.data["prom", "Pr(>|t|)"]
wear_gloves.rf.prom.or <- exp(wear_gloves.rf.prom.b)

wear_gloves.rf.prev.b <- wear_gloves.rf.data["prev", "Estimate"]
wear_gloves.rf.prev.se <- wear_gloves.rf.data["prev", "Std. Error"]
wear_gloves.rf.prev.t <- wear_gloves.rf.data["prev", "t value"]
wear_gloves.rf.prev.df <- round(summary(wear_gloves.rf)$df[2], digits = 0)
wear_gloves.rf.prev.p <- wear_gloves.rf.data["prev", "Pr(>|t|)"]
wear_gloves.rf.prev.or <- exp(wear_gloves.rf.prev.b)

confint(wear_gloves.rf)
```

```{r avoid_places_no_socdist}
avoid_places_no_socdist.rf <- lm(avoid_places_no_socdist ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(avoid_places_no_socdist.rf)
avoid_places_no_socdist.rf.data <- summary(avoid_places_no_socdist.rf)$coefficients

avoid_places_no_socdist.rf.prom.b <- avoid_places_no_socdist.rf.data["prom", "Estimate"]
avoid_places_no_socdist.rf.prom.se <- avoid_places_no_socdist.rf.data["prom", "Std. Error"]
avoid_places_no_socdist.rf.prom.t <- avoid_places_no_socdist.rf.data["prom", "t value"]
avoid_places_no_socdist.rf.prom.df <- round(summary(avoid_places_no_socdist.rf)$df[2], digits = 0)
avoid_places_no_socdist.rf.prom.p <- avoid_places_no_socdist.rf.data["prom", "Pr(>|t|)"]
avoid_places_no_socdist.rf.prom.or <- exp(avoid_places_no_socdist.rf.prom.b)

avoid_places_no_socdist.rf.prev.b <- avoid_places_no_socdist.rf.data["prev", "Estimate"]
avoid_places_no_socdist.rf.prev.se <- avoid_places_no_socdist.rf.data["prev", "Std. Error"]
avoid_places_no_socdist.rf.prev.t <- avoid_places_no_socdist.rf.data["prev", "t value"]
avoid_places_no_socdist.rf.prev.df <- round(summary(avoid_places_no_socdist.rf)$df[2], digits = 0)
avoid_places_no_socdist.rf.prev.p <- avoid_places_no_socdist.rf.data["prev", "Pr(>|t|)"]
avoid_places_no_socdist.rf.prev.or <- exp(avoid_places_no_socdist.rf.prev.b)

confint(avoid_places_no_socdist.rf)
```

```{r clean_disinfect}
clean_disinfect.rf <- lm(clean_disinfect ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(clean_disinfect.rf)
clean_disinfect.rf.data <- summary(clean_disinfect.rf)$coefficients

clean_disinfect.rf.prom.b <- clean_disinfect.rf.data["prom", "Estimate"]
clean_disinfect.rf.prom.se <- clean_disinfect.rf.data["prom", "Std. Error"]
clean_disinfect.rf.prom.t <- clean_disinfect.rf.data["prom", "t value"]
clean_disinfect.rf.prom.df <- round(summary(clean_disinfect.rf)$df[2], digits = 0)
clean_disinfect.rf.prom.p <- clean_disinfect.rf.data["prom", "Pr(>|t|)"]
clean_disinfect.rf.prom.or <- exp(clean_disinfect.rf.prom.b)

clean_disinfect.rf.prev.b <- clean_disinfect.rf.data["prev", "Estimate"]
clean_disinfect.rf.prev.se <- clean_disinfect.rf.data["prev", "Std. Error"]
clean_disinfect.rf.prev.t <- clean_disinfect.rf.data["prev", "t value"]
clean_disinfect.rf.prev.df <- round(summary(clean_disinfect.rf)$df[2], digits = 0)
clean_disinfect.rf.prev.p <- clean_disinfect.rf.data["prev", "Pr(>|t|)"]
clean_disinfect.rf.prev.or <- exp(clean_disinfect.rf.prev.b)

confint(clean_disinfect.rf)
```

### Perceived Covid-19 Threat Level

```{r covid_threat_personal}
covid_threat_personal.rf <- lm(covid_threat_personal ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(covid_threat_personal.rf)
covid_threat_personal.rf.data <- summary(covid_threat_personal.rf)$coefficients

covid_threat_personal.rf.prom.b <- covid_threat_personal.rf.data["prom", "Estimate"]
covid_threat_personal.rf.prom.se <- covid_threat_personal.rf.data["prom", "Std. Error"]
covid_threat_personal.rf.prom.t <- covid_threat_personal.rf.data["prom", "t value"]
covid_threat_personal.rf.prom.df <- round(summary(covid_threat_personal.rf)$df[2], digits = 0)
covid_threat_personal.rf.prom.p <- covid_threat_personal.rf.data["prom", "Pr(>|t|)"]

covid_threat_personal.rf.prev.b <- covid_threat_personal.rf.data["prev", "Estimate"]
covid_threat_personal.rf.prev.se <- covid_threat_personal.rf.data["prev", "Std. Error"]
covid_threat_personal.rf.prev.t <- covid_threat_personal.rf.data["prev", "t value"]
covid_threat_personal.rf.prev.df <- round(summary(covid_threat_personal.rf)$df[2], digits = 0)
covid_threat_personal.rf.prev.p <- covid_threat_personal.rf.data["prev", "Pr(>|t|)"]

confint(covid_threat_personal.rf)
```

```{r covid_threat_peers}
covid_threat_peers.rf <- lm(covid_threat_peers ~ prom + prev + agegroup.num.c + pol_orient.num.c, data = rf)
summary(covid_threat_peers.rf)
covid_threat_peers.rf.data <- summary(covid_threat_peers.rf)$coefficients

covid_threat_peers.rf.prom.b <- covid_threat_peers.rf.data["prom", "Estimate"]
covid_threat_peers.rf.prom.se <- covid_threat_peers.rf.data["prom", "Std. Error"]
covid_threat_peers.rf.prom.t <- covid_threat_peers.rf.data["prom", "t value"]
covid_threat_peers.rf.prom.df <- round(summary(covid_threat_peers.rf)$df[2], digits = 0)
covid_threat_peers.rf.prom.p <- covid_threat_peers.rf.data["prom", "Pr(>|t|)"]

covid_threat_peers.rf.prev.b <- covid_threat_peers.rf.data["prev", "Estimate"]
covid_threat_peers.rf.prev.se <- covid_threat_peers.rf.data["prev", "Std. Error"]
covid_threat_peers.rf.prev.t <- covid_threat_peers.rf.data["prev", "t value"]
covid_threat_peers.rf.prev.df <- round(summary(covid_threat_peers.rf)$df[2], digits = 0)
covid_threat_peers.rf.prev.p <- covid_threat_peers.rf.data["prev", "Pr(>|t|)"]

confint(covid_threat_peers.rf)
```
